\documentclass[11pt]{article}

% ---------------------------------------------------------------------------
% arXiv-ready LaTeX source for:
%   Ground-Truth Measurement of the Atomic-MEV Opportunity Surface on Post-PBS
%   BNB Smart Chain (dual-strategy: cross-DEX backrun + sandwiching)
% Mirrors the markdown in paper.md / 00..60-*.md. \cite keys match references.bib.
% Build:  pdflatex paper && bibtex paper && pdflatex paper && pdflatex paper
% All result numbers are final: the consolidated geth-sim10 backrun run
% (3,000 sampled blocks), the consolidated geth-sim15 sandwich run
% (2,550 sampled blocks), the COMPLETED geth-sim20 realizability run
% (315,750 processed blocks; 45/96,064 = 0.0468% by count) -- geth-sim16
% was the 2,100-block realizability pilot, and geth-sim20 also supplies the
% Phase-2 matched-footprint / serialization / trace-probe numbers -- and the
% live geth-sim17 censorship-differential run (settle window K=256, 954/958
% historical drops verified mined-later).
% ---------------------------------------------------------------------------

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb}
\usepackage{booktabs}
\usepackage{array}
\usepackage{longtable}
\usepackage[hidelinks]{hyperref}
\usepackage{url}
\usepackage{xcolor}

\newcommand{\code}[1]{\texttt{#1}}

\title{Receipt-Exact Measurement of the Atomic-MEV Surface on Post-PBS
BNB Smart Chain: The Realized Independent-Searcher Edge Is Vanishingly Small}

\author{Alessio Rocchi}
\date{June 2026}

\begin{document}
\maketitle

\begin{abstract}
Empirical studies of decentralized-exchange (DEX) MEV estimate opportunities
analytically from constant-function-market-maker (CFMM) closed forms---which
approximate fees, ignore tick-crossing in concentrated-liquidity (V3) pools, cannot
account for reverts, hooks, or rounding, and price each MEV \emph{category} on a
different dataset---so they systematically over-count and make cross-strategy
comparison unreliable. \textbf{This paper makes one epistemic structure explicit up
front: we \emph{measure} three things and \emph{infer} a fourth.} We measure (1)~the
\emph{ex-post} atomic-MEV opportunity surface with a receipt-exact oracle, (2)~the
in-block \emph{real-competitor} capture rate, and (3)~the censorship-differential; from
these we \textbf{infer}---we do \emph{not} directly measure---the edge available to an
\emph{independent} searcher, via the explicit, falsifiable \emph{unrealized $\neq$
available} mechanism (\S6.8), because the PBS-submission path is disarmed and never
exercised (no independent bundle is ever actually placed). The headline capture window
is a \emph{single $\sim$2.5-day regime} (a 14-day collection early-stopped on state
growth), so generalization across volatility regimes is future work.
\textbf{(a)~Instrument and contribution.} Rather than approximate execution, we
\emph{execute}: an in-process \emph{SimEngine} re-applies real BNB Smart Chain (BSC)
blocks on a copy of the parent state via the node's own \code{core.ApplyTransaction},
used as a \emph{single} ground-truth instrument to price \emph{both} atomic
categories---cross-DEX backrun arbitrage and sandwiching---on the \emph{same} blocks and
the \emph{same} victim stream, valuing every opportunity with the actual pool bytecode
(V3 hops EVM-valued via in-process QuoterV2; V2 hops by the exact integer closed form,
receipt-validated for V2 swaps but still analytic, see T8). Backrun is detected at the
correct \textbf{intra-block transient} (immediately after each victim swap, the only
state where it exists); sandwiching is \textbf{constructed} on copied state (a synthetic
attacker funded by direct ERC20 storage writes, a conservative bias that can only
understate profit), routing frontrun and backrun to the victim's \emph{actual} pool with
the \emph{real} victim transaction replayed between. \textbf{(b)~Validation.} Simulated
receipts match the canonically stored receipts \emph{exactly}---status, gas, cumulative
gas, and every log---5/5 PASS on real mainnet blocks (100--151 txs each) and
\textbf{500/500 in Phase-2}; this certifies the \textbf{replay} (the counterfactual
sandwich \textbf{construction} has no ground-truth receipt and is argued conservative,
not receipt-validated). \textbf{(c)~Headline results.} The two strategies diverge
sharply. \textbf{Cross-DEX backrun on the deep WBNB/stable hub is sub-gas}: over
$3{,}000$ blocks the EVM confirms $803$ gross-positive cycles but only \textbf{$15$
($1.9\%$) clear the $\sim$\$0.50 gas gate} ($280$k gas $\times$ $3$ gwei), $\sim$\$10
total. \textbf{Sandwiching the long tail is not}: over $2{,}550$ blocks and $33{,}525$
victim swaps we find $1{,}735$ gross-positive and \textbf{$1{,}162$ ex-post net-positive
sandwiches} (median gross \$1.78, max \$430.50), totalling \textbf{$35.08$ BNB
($\sim$\$20{,}200)}---a gap of \textbf{$\sim$91$\times$ in net-positive count and
$\sim$2{,}040$\times$ in raw aggregate value} (different block counts, $3{,}000$ vs
$2{,}550$; $\sim$2{,}400$\times$ per-block normalized, and $458\times$ on a matched,
basis-aligned footprint, \S\ref{sec:contrast-matched}). The in-block counterfactual then
measures \emph{realized} capture: over the completed multi-day window, captured
sandwiches number \textbf{45 of $96{,}064$ ($0.0468\%$ by count, Wilson $95\%$ CI
[$0.0350\%$, $0.0627\%$]; $0.0078\%$ by value)} over \textbf{$315{,}750$ processed blocks
spanning 2.5 days} (2026-06-09 04:27 -- 2026-06-11 17:29, chain heights
$\sim$102.99M--103.63M), with \textbf{25 captures by repeated address} (one address
0xCF2e..C842 $=$ 17 of 45, $38\%$), \textbf{20 by unknown, 0 by builder}; and the
censorship-differential is \textbf{$\hat D = 0$} after a chain-verified settle window
($99.6\%$ of apparent public ``drops'' are merely delayed inclusion, not censorship).
Cross-tx sandwiching has receded under validator/builder filtering and private order
flow (BEP-322; two latency-advantaged builders, 48Club and BlockRazor, see private flow
ahead of the public mempool and capture $\sim$$90\%$ of MEV), the same regime that would
exclude an independent's sandwich---so the \emph{inferred} realized independent
atomic-searcher edge is \textbf{vanishingly small}, bounded above by the measured
$0.0468\%$-by-count / $0.0078\%$-by-value capture rate and below by zero on the windows
measured, with the surviving surface in the long tail, not the deep markets the backrun
literature studies. \textbf{(d)~Limits.} The independent edge is \emph{inferred}, not
directly measured (the PBS-submission path is never exercised); the capture window is a
single early-stopped $\sim$2.5-day regime; and backrun (a fixed 12-pool deep
WBNB/stablecoin hub) and sandwich (any long-tail WBNB-paired pool) are measured on
intentionally different scopes, so the $91\times$--$2{,}040\times$ gap reflects both
strategy profitability \emph{and} that portfolio difference. The transferable
contribution is the validated ground-truth instrument and protocol. During development
we found and fixed \textbf{five integrity catches} in the detectors (units bug;
realizability false-zero; censorship estimand-inversion; censorship delayed-vs-censored
conflation; backrun-any decimal-mismatch sanity-cap fire), documented in the methods for
reproducibility.
\end{abstract}

\paragraph{Contributions.}
\begin{enumerate}
  \item A receipt-exact, in-process simulation methodology (SimEngine) that
    re-executes real blocks on copied node state via \code{core.ApplyTransaction}
    and matches stored receipts byte-for-byte (5/5 PASS)---ground-truth execution,
    strictly more faithful than analytic CFMM for V3 / fee-on-transfer / hooks /
    reverts---used as the \emph{single} valuation substrate for \emph{both} atomic
    MEV categories we measure.
  \item A ground-truth valuation oracle for \textbf{backrun} (Stage~B):
    every candidate cross-venue cycle valued by the actual pool/Quoter bytecode---V3
    hops by in-process QuoterV2 (EVM-valued on the exact intermediate state), V2 hops by
    the exact integer closed form (receipt-validated for V2 swaps on real blocks, but
    still an analytic closed form, not full re-execution; see T8)---with
    optimal-input search, evaluated at the correct intra-block transient (post-block
    evaluation is \emph{not} a backrun test---intra-block competitors re-align
    prices).
  \item A full-EVM ground-truth \textbf{sandwich} constructor: a synthetic attacker
    funded by direct storage writes (hardcoded $+$ runtime-probed ERC20 slots),
    frontrun/backrun routed to the victim's actual pool (K-safe direct
    \code{pair.swap} for any V2 fork; the real V3 SwapRouter for Pancake V3), the
    real victim tx replayed between, profit read off the EVM in a single BNB-priced
    numeraire---the first (to our knowledge) receipt-exact \emph{per-block census} of
    the sandwich surface (complementing per-target executing optimizers such as
    Lanturn \cite{babel2023lanturn}, which construct and EVM-simulate
    sandwich/arbitrage strategies for a chosen contract rather than censusing every
    victim swap in a block).
  \item \textbf{The first (to our knowledge) controlled backrun-vs-sandwich
    measurement on one instrument and one victim stream}: same blocks, same EVM
    valuation, same cost
    model---turning a cross-paper comparison into a single controlled experiment.
    Note the two strategies are measured on \emph{different scopes} (backrun on a fixed
    12-pool deep WBNB/stablecoin hub, sandwich across any long-tail WBNB-paired pool);
    this scope difference is intentional (long-tail sandwiching is where ex-post value
    concentrates) but means the resulting gap reflects both strategy profitability
    \emph{and} the portfolio difference.
    Prior executing tools (e.g.\ Lanturn \cite{babel2023lanturn}) EVM-evaluate
    constructed strategies but optimize one target at a time; we instead hold a single
    per-block victim stream fixed and price \emph{both} atomic categories on it.
  \item A measurement of the independent-searcher atomic-MEV surface: backrun is
    frequent but \textbf{sub-gas} ($15$ of $803$ net-positive over $3{,}000$ blocks,
    $\sim$\$10) on the deep hub; sandwiching the long tail is \textbf{substantial
    ex-post} ($1{,}162$ of $1{,}735$ net-positive over $2{,}550$ blocks, $35.08$ BNB
    $\approx$ \$20{,}200) but \textbf{realized by only a small measured fraction}
    (an earlier geth-sim16 pilot corroborated $\approx$$0.07\%$ by count and
    $\approx$$0.016\%$ by value over $34{,}200$ blocks, slightly above the final measured rate from
    the completed window, $0.0468\%$ by count ($45/96{,}064$, Wilson CI [$0.0350\%$, $0.0627\%$]) and $0.0078\%$ by value)---establishing
    that while ex-post sandwiching dominates ex-post backrun by $\sim$91$\times$ in
    count and $\sim$2{,}040$\times$ in raw aggregate value (as measured on their
    respective scopes; block counts differ: $2{,}550$ sandwich vs $3{,}000$ backrun;
    per-block normalized value ratio $\sim$2{,}400$\times$; see
    \S\ref{sec:contrast-matched} for the matched-footprint, universe-matched
    basis-aligned contrast: $\sim$458$\times$ in BNB-denominated value/block, price-free),
    the realized edge for an independent across both strategies is
    much smaller.
  \item The ex-post sandwich surface density ($0.35$--$0.46$ net-positive per block over
    our measurement window) as the baseline for the in-block counterfactual and the
    ex-post-vs-realized comparison; we deliberately do \emph{not} report an annualized
    extrapolation, since annual scaling is unreliable given diurnal/volatility variation
    and the per-victim concurrent same-pool over-count (\S\ref{sec:realizable}).
  \item \textbf{A ground-truth in-block counterfactual} that converts ex-post
    existence into a \emph{measured} realizability: for each ex-post opportunity it
    detects whether a real competitor already captured it in the canonical block
    (conjunctive bracket $+$ same-actor $+$ profit-corroboration gates, conservative
    by construction, with an auditable funnel). A $2{,}100$-block window finds $0$ of
    $735$ ex-post sandwiches realized (capture rate $0.00$); a longer multi-day
    collection has anchored the rate at $\approx$$0.07\%$ by count and
    $\approx$$0.016\%$ by value (geth-sim16 pilot over $34{,}200$ blocks, $7$ captures
    of $\sim$$10{,}190$ ex-post opportunities; a later $152{,}650$-block pilot anchored
    $10$ captures); these earlier, smaller windows corroborate and sit slightly above the final measured
    capture rate, CI, and repeat-actor structure of \textbf{45 of $96{,}064$
    ($0.0468\%$ by count, Wilson $95\%$ CI [$0.0350\%$, $0.0627\%$]; $0.0078\%$ by value),
    with 25 captures by repeated address (0xCF2e..C842 $=$ 17 of 45, $38\%$), 20 by
    unknown, 0 by builder, over $315{,}750$ blocks (2026-06-09 04:27 -- 2026-06-11 17:29)},
    establishing nonzero but small realization
    relative to the ex-post surface---the short-window zero was a sampling artifact,
    consistent with the filtering $+$ private-flow regime and cross-referenced with a
    $1{,}500$-block pool-agnostic scan showing cross-tx sandwiching is rare. A
    separately measured trace-probe over $30{,}100$ blocks finds the identification
    gap is \textbf{bounded at zero} on that window: $1{,}585$ structural round-trips
    and $2$ sweeps exist as patterns but carry zero positive ex-post net profit
    (\code{upperBoundMissedRealizedWei}$=0$; see \S\ref{sec:realizability}). Thus the
    realized atomic edge is substantially smaller than the ex-post surface by direct
    measurement of real-competitor capture; the independent-searcher edge follows by the
    \emph{unrealized $\neq$ available} inference (\S6.1).
  \item A careful realizability / threats discussion separating ex-post existence
    (what we prove) from realizable capture (which we now measure), uniform across
    both strategies, including the \emph{unrealized $\neq$ available} point (developed in
    \S\ref{sec:realizable}), with an explicit statement of what would change the conclusion.
\end{enumerate}

% ===========================================================================
\section{Introduction}

\subsection{Maximal Extractable Value and the measurement problem}
Maximal Extractable Value (MEV)---the profit a party can extract by including,
excluding, or reordering transactions within the blocks it produces or
influences---has grown into a structural feature of every major smart-contract
chain since Daian et al.\ introduced the concept and documented priority-gas
auctions and consensus-layer instability in \emph{Flash Boys 2.0}
\cite{daian2020flashboys}. A large share of MEV is \emph{atomic arbitrage}: a
single transaction that buys cheaply on one DEX and sells dearly on another. When
it trails the user swap that \emph{created} the discrepancy, it is a \emph{backrun}.

The empirical literature---cyclic arbitrage \cite{wang2021cyclic}, quantifying
blockchain extractable value \cite{qin2022quantifying}, front-running
\cite{torres2021frontrunner}, large-scale measurement \cite{mclaughlin2023arbitrage}---
shares a rarely-examined choice: \textbf{opportunities are estimated analytically}.
A study reads reserves, applies a CFMM closed form (usually Uniswap V2 $x\cdot y=k$),
and reports the implied trade. This embeds approximations that distort the answer:
it assumes $x\cdot y=k$ even for pools that do not obey it (concentrated-liquidity
V3 \cite{adams2021uniswapv3}, stableswap); it cannot see \emph{reverts}; it ignores
\emph{fee-on-transfer tokens, hooks, and rounding}; and it conflates ex-post with
realizable opportunity. The net effect is that analytic studies \textbf{over-count}.
Even at the detection layer, Zhang et al.\ show a naive negative-cycle scan surfaces
a fraction of what a better graph transform finds \cite{zhang2024improved}; at the
valuation layer the gap to exact, fee-and-tick-accurate profit is larger still.

\subsection{Our instrument: receipt-exact in-process re-execution}
Rather than approximate execution, \textbf{we execute}. We run a full BSC node
(bsc-geth v1.7.3, snapshot-seeded, 64-core / 125\,GB host) and build an in-process
\emph{SimEngine} that applies a block's transactions on a \emph{copy} of the parent
state through the node's own \code{core.ApplyTransaction}---the identical path the
canonical processor uses. The canonical state is never mutated.

The SimEngine is \textbf{validated against ground truth}: we replay real mainnet
blocks and compare simulated receipts to the stored receipts. They match
\emph{exactly}---status, gas used, cumulative gas used, and every log's address,
topics, and data---5/5 PASS on blocks around height 101.83M with 100--151 txs each.
This \emph{is} execution, with a receipt-level certificate. For V3 this is decisive:
rather than re-implement \code{TickMath}/\code{SwapMath}/\code{SqrtPriceMath} we let
the pool bytecode be its own arbiter \cite{adams2021uniswapv3,diamandis2023routing}.

\subsection{The post-PBS BSC regime, and why this result is interesting}
BSC is high-throughput, deeply liquid in a small hub (WBNB, USDT, USDC, USD1, BUSD),
and recently underwent a proposer--builder separation (PBS) transition via BEP-322
\cite{bep322}: no relay, whitelisted builders, private order flow ahead of the
public mempool. Wang et al.\ \cite{wang2025binance} report that two builders
(48Club, BlockRazor) produce most blocks and capture most MEV; the dominant strategy
is short (2--3 swap) cycles on the WBNB/stablecoin hub; opportunities live
$\sim$100--400\,ms; public-mempool transactions reach external searchers tens of ms
\emph{after} builder bundles.

This is the backdrop against which we ask, more broadly than the backrun literature
does, \textbf{what the atomic-MEV opportunity surface available to an
\emph{independent} searcher actually looks like on post-PBS BSC}---across both of the
atomic categories a non-builder could in principle contest. We split the primary
question into two---with a methodological third (RQ3) that falls out of the
instrument. \textbf{RQ1: is there any net-positive independent-searcher
\emph{backrun} edge left on BSC's major pools?} And \textbf{RQ2: how does that
compare, on the \emph{same} instrument and the \emph{same} victim stream, to
\emph{sandwiching}---the dominant atomic MEV category on BSC by value (roughly half
of measured BSC MEV)?} Treating both on one ground-truth substrate is the
methodological move that makes the comparison meaningful, because the existing
literature prices each category on a different dataset with a different (analytic)
model.

\paragraph{What we measure, and what we infer (stated up front).} Our design identifies
three quantities directly and a fourth only by inference, and we keep that boundary
explicit throughout. We \emph{measure}: (1)~the \emph{ex-post} atomic-MEV opportunity
surface, receipt-exact, via the EVM oracle; (2)~the \emph{in-block real-competitor
capture rate}, by detecting whether a real competitor already took each ex-post
opportunity in the canonical block; and (3)~the \emph{censorship-differential} $D$, the
one point-identified, structurally-reachable extraction estimand. We do \emph{not}
directly measure the edge an \emph{independent} searcher would realize: the
PBS-submission path is disarmed and never exercised, so no independent bundle is ever
actually placed. We \emph{infer} that edge from the three measured surfaces through the
explicit, falsifiable \emph{unrealized $\neq$ available} mechanism (\S6.1, \S6.8), and we
state the condition that would overturn it. Finally, the headline capture window is a
\emph{single $\sim$2.5-day regime}---a 14-day collection early-stopped on state
growth---so generalization across volatility regimes is future work, not a claim we make
here.

For RQ1, our naive baseline (three deep Pancake V2 pools, exact closed-form optimal
input, 250k-gas / 3-gwei gate, zero builder bid) finds \textbf{zero profitable
backruns over $5{,}100$ blocks}; a cross-DEX V2 graph extension finds \textbf{zero
candidates over $2{,}950$ blocks}. \emph{But they measure the wrong thing}: both
evaluate against \emph{post-block} reserves, where cross-venue prices are already
re-aligned by intra-block competitors. Backrun MEV lives in the transient state
immediately \emph{after} a victim swap; end-of-block evaluation misses it. These
post-block zeros quantify \emph{standing} arbitrage, not backrun-able
transients---a realization that reframes the study.

\subsection{The correct experiment: intra-block, EVM-valued}
The SimEngine re-executes each block transaction-by-transaction, so we hook in
\textbf{after every transaction that emits a watched-pool \code{Swap}}, snapshot
reserves there, and detect+value at the only state where a backrun could exist. The
final model: (1) builds a token graph over a verified 12-pool multi-DEX set (six V2:
three Pancake, three Biswap; six Pancake V3 across tiers 100/500/2500), edges
weighted $-\ln(r_{uv}(1-\text{fee}))$; (2) runs negative-cycle detection (Stage~A,
\emph{detection only}, marginal prices) for cycles of length $2..K$ from WBNB; (3)
\textbf{values every candidate with the EVM (Stage~B), the sole oracle}: V2 hops by
the closed form, V3 hops by an in-process PancakeSwap \emph{QuoterV2} call on the
exact intermediate \code{state.Copy()}, with optimal input by golden-section over
EVM probes; (4) applies $\text{net} = \text{gross} - \sum\text{gas} - \text{bid}$
with measured per-cycle gas ($\sim$280k) at 3\,gwei ($\approx$\$0.50), assuming
capital-free flash funding \cite{qin2021flashloans}, and emits a gross-profit
distribution, break-even gas price, and a $\{0,0.1,0.3,1,3\}$ gwei sweep.
\textbf{RQ3} follows: the gross-positive$\to$net-positive collapse measures the
analytic over-count.

The same intra-block victim stream answers \textbf{RQ2} with no change of
instrument. For \emph{every} watched-pool victim swap the SimEngine surfaces, we do
not merely look for a trailing arbitrage---we \textbf{construct the adversarial
sandwich}: on a fresh copy of the pre-swap state we fund a synthetic attacker,
insert an optimally-sized frontrun \emph{in the victim's own pool}, replay the
\emph{real} victim transaction against the degraded reserves, close with a backrun,
and read the attacker's profit straight off the EVM (\S\ref{sec:sandwich-method}).
Because the construction routes to the victim's actual pool by a K-safe direct
\code{pair.swap}, it generalizes beyond the deep hub to \textbf{any V2-fork pool in
the long tail}---exactly where, our own backrun runs hint, the volume actually is
(the deep pools were quiet). This lifts the study from ``is backrun profitable on
the hub?'' to ``which atomic strategy, backrun or sandwich, carries the
independent-searcher edge, and where?''---and the answer (RQ2) turns out to be larger
for sandwiching than backrun by roughly two-to-three orders of magnitude.

\subsection{Summary of findings}
\begin{itemize}
  \item The SimEngine reproduces real mainnet receipts exactly (\textbf{5/5 PASS},
    100--151 txs each): \emph{one} ground-truth execution instrument, used for
    \emph{both} strategies.
  \item \textbf{Backrun (deep hub).} The naive deep-pool model finds
    \textbf{$0/5{,}100$ blocks} and the cross-DEX V2 graph \textbf{$0/2{,}950$
    blocks} (both \emph{post-block}, not valid backrun tests). The correct
    intra-block detector $+$ EVM oracle, over \textbf{$3{,}000$ sampled blocks},
    confirms \textbf{$803$ ground-truth gross-positive cross-venue cycles
    ($\sim$$0.27$ per block), of which only $15$ ($1.9\%$) are ex-post net-positive}
    at 3 gwei---$\sim$1 per 200 sampled blocks, $0.0172$ BNB ($\sim$\$10) total; the
    other $788$ sit below the $\sim$\$0.50 gas floor. Frequent, real, but
    \textbf{overwhelmingly sub-gas}.
  \item \textbf{Sandwich (long tail).} The EVM-constructed three-leg attack, over
    \textbf{$2{,}550$ sampled blocks} examining \textbf{$33{,}525$ victim swaps},
    finds \textbf{$1{,}735$ gross-positive and $1{,}162$ ex-post net-positive
    sandwiches} at 3 gwei ($\sim$$0.46$ per block), totalling \textbf{$35.08$ BNB
    ($\sim$\$20{,}200)}; median gross \$1.78, p90 \$31.6, max \$430.50. The $1{,}162$
    net-positive $=67.0\%$ of gross-positive after gas$+$flash; $69.0\%$ ($1{,}197$)
    clear the 3-gwei gas gate before the flash premium---entirely on long-tail
    WBNB-paired pools.
  \item \textbf{The contrast (headline).} Same instrument, same victim stream:
    sandwiching yields \textbf{$\sim$91$\times$ more net-positive opportunities per
    block and $\sim$2{,}040$\times$ more total value in raw aggregate} (note block
    counts differ: $2{,}550$ sandwich vs $3{,}000$ backrun; $\sim$2{,}400$\times$
    per-block normalized) than backrun. The independent
    searcher's atomic-MEV edge is a \textbf{long-tail sandwiching phenomenon, not a
    deep-pool backrun one}.
  \item \textbf{Ex-post surface density (no annual extrapolation).} The ground-truth
    \emph{ex-post} sandwich surface runs at $0.35$--$0.46$ net-positive sandwiches per
    block over our measurement window. We deliberately do \emph{not} annualize it:
    annual scaling is unreliable given diurnal/volatility variation and the per-victim
    concurrent same-pool over-count (\S\ref{sec:realizable}). The density is the baseline
    against which the realized fraction (\S\ref{sec:realizability}) is measured---the
    ex-post-vs-realizable gap is the finding (\S\ref{sec:extval}), not an absolute annual
    figure.
  \item \textbf{Realizability (in-block counterfactual).} Of the \textbf{735 ex-post
    sandwich opportunities} in a $2{,}100$-block window, \textbf{0 were captured} by a
    real cross-tx sandwich (capture rate $0.00$ in that small window, auditable funnel:
    $1{,}077$ brackets $\to$ $79$ same-actor $\to$ $0$ corroborated). A longer
    collection anchors the realized capture at $\approx$$0.07\%$ by count
    and $\approx$$0.016\%$ by value (geth-sim16 pilot over $34{,}200$ blocks: $7$
    captures of $\sim$$10{,}190$ ex-post opportunities; a later $152{,}650$-block pilot
    anchored $10$ captures); these earlier, smaller windows corroborate and sit slightly above the \textbf{final measured capture rate, CI, and
    repeat-actor count} over the completed multi-day, multi-volatility window,
    \textbf{45 of $96{,}064$ ($0.0468\%$ by count, Wilson $95\%$ CI [$0.0350\%$,
    $0.0627\%$]; $0.0078\%$ by value), measured over $315{,}750$ processed blocks
    (2026-06-09 04:27 -- 2026-06-11 17:29, $\sim$61 hours, chain heights
    $\sim$102.99M--103.63M); 25 captures by repeated address (0xCF2e..C842 $=$ 17 of 45,
    $38\%$), 20 by unknown, 0 by builder}, concentrated in repeated addresses and
    structures matching blind-spot patterns (mid-tx sweep, non-flat round-trips)---
    establishing that the small-window zero was a sampling artifact and realization is
    nonzero but a small fraction of the ex-post surface. A separately measured Phase-2
    trace-probe over $30{,}100$ blocks finds $1{,}585$ structural round-trips and $2$
    sweeps as patterns but with \code{upperBoundMissedRealizedWei}$=0$---\textbf{the
    identification gap is bounded at zero on that window}; the blind-spot pattern is
    demographic, not economic (\S\ref{sec:realizability}). Cross-tx sandwiching is rare
    in realized BSC activity; realized MEV is dominated by single-transaction atomic
    arbs. \emph{Unrealized $\neq$ available}: the small realized fraction is consistent
    with the filtering $+$ private-flow regime that suppresses sandwiching for everyone,
    including an independent (corroborated by the trace-probe upper-bound of zero on
    this window).
  \item \textbf{Censorship-differential (the reachable estimand).} The one
    point-identified, structurally-reachable estimand---the value a builder leaves by
    \emph{dropping} public, orthogonal, profitable opportunities---is \textbf{$\hat D = 0$}
    after a chain-verified settle window; \textbf{$99.6\%$} of apparent public ``drops''
    were merely \emph{delayed inclusion} (mined a few blocks later), not censorship. The
    public residual is empty too.
  \item \textbf{Implementation bugs / integrity catches (reproducibility).} During
    development we found and fixed \textbf{five integrity catches} in the detectors
    (detailed in \S3 and \S\ref{sec:contrast-matched}), each documented in the methods
    so the results are reproducible.
\end{itemize}

The conclusion: on post-PBS BSC the \emph{ex-post} atomic-MEV surface looks like it
has \textbf{migrated from deep-pool backrun (15 of 803 net-positive, $\sim$\$10) to
long-tail sandwiching} (1{,}162 net-positive, $\sim$\$20{,}200 ex-post)---but
\emph{realized}, both are far less capturable by an independent. Backrun on the deep hub
is sub-gas; the long-tail sandwich surface, though large ex-post, is realized by
\textbf{only a small measured fraction} (final measured rate $0.0468\%$ by count ($45/96{,}064$, Wilson $95\%$ CI [$0.0350\%$, $0.0627\%$]) and $0.0078\%$ by value over the completed $315{,}750$-block window; earlier smaller windows corroborated this---the geth-sim16 pilot at $7$ of
$\sim$$10{,}190$ $\approx$ $0.07\%$ by count, $\approx$$0.016\%$ by value over
$34{,}200$ blocks) and would face the same filtering barriers. The short-window zero
(capture rate 0 over 2{,}100 blocks) was a sampling artifact corrected by the
longer-window collection. Under BEP-322 two
latency-advantaged builders (48Club, BlockRazor) produce most blocks, see private
flow ahead of the public mempool, and capture $\sim$$90\%$ of MEV
\cite{bep322,wang2025binance}. So the independent atomic-searcher edge in realized terms
is \emph{vanishingly small}---bounded above by the measured $0.0468\%$-by-count
rate ($0.0078\%$ by value; earlier smaller windows corroborated slightly higher at $\approx$0.07\%) and below by zero on the windows measured---and we \emph{infer} it is not available to an independent via the
\emph{unrealized $\neq$ available} mechanism (\S6.1), not from a direct measurement of
independent capture. The transferable
contribution is the
\emph{instrument and protocol}: validated ground-truth valuation (V3 hops EVM-valued, V2 hops closed-form; T8) that prices
every atomic category on one substrate, evaluated at the correct intra-block
transient (backrun gross$\to$net collapse $803 \to 15$---the quantitative case
against analytic CFMM over-counting, especially for V3), a controlled
backrun-vs-sandwich contrast (with scope caveats: deep hub vs. long tail),
and an in-block counterfactual that turns ``ex-post existence'' into measured
realizability across an extended window.

% ===========================================================================
\section{Related Work}

We organize prior work into seven threads: (i)~MEV foundations, (ii)~cyclic /
graph-based arbitrage detection, (iii)~convex-optimization routing and optimal
sizing over CFMMs, (iv)~concentrated liquidity, (v)~flash loans / capital-free
execution, (vi)~sandwich attacks and their concentrated-liquidity profitability, and
(vii)~the BSC PBS regime that frames the interpretation.

\subsection{MEV foundations}
\emph{Flash Boys 2.0} \cite{daian2020flashboys} introduced MEV, priority-gas
auctions, and time-bandit attacks. Heimbach and Wattenhofer's SoK
\cite{heimbach2022sok} systematizes reordering manipulations and defenses (private
flow, fair ordering, encrypted mempools) the BSC PBS regime partially instantiates.
Qin et al.\ \cite{qin2022quantifying} quantify blockchain extractable value and the
consensus-security incentive to fork; Torres et al.\ \cite{torres2021frontrunner}
analyze $\sim$11M blocks for $\sim$200k front-running attacks. \emph{Position:} these
works motivate \emph{why} arbitrage MEV is worth measuring; we contribute a
measurement \emph{instrument}---receipt-exact realized value rather than analytic
inference. The closest non-analytic prior art is Lanturn \cite{babel2023lanturn},
whose adaptive-learning optimizer constructs MEV-extracting transaction sequences and
\emph{executes them on real chain state without modification} (over
Sushiswap/Uniswap V2/V3/Aave), valuing sandwich, arbitrage, and backrun strategies by
simulation rather than closed form. Lanturn optimizes value for a \emph{chosen target
contract}; we instead run a \emph{per-block, full-node census} that prices every
watched victim swap in every block. Our instrument and Lanturn are thus
complementary: per-target optimizer vs.\ per-block opportunity census, both refusing
the analytic CFMM surrogate.

\subsection{Cyclic and graph-based detection}
The standard technique adapts FX negative-cycle search: tokens as nodes, ordered
pool-directions as edges of weight $-\ln(r_{uv}(1-\text{fee}))$; a profitable cycle
is a negative cycle, found by Bellman--Ford ($O(VE)$), SPFA, or Johnson's. Wang et
al.\ \cite{wang2021cyclic} give the empirical framing ($>$\$138M cyclic-arb
revenue). Known limits for profit: marginal-rate weights certify only an
infinitesimal trade; vanilla Bellman--Ford returns one arbitrary cycle; the signal
is a percentage. Zhang et al.\ \cite{zhang2024improved} address these with a
line-graph + Modified MBF pass; McLaughlin et al.\ \cite{mclaughlin2023arbitrage}
are the large-scale precedent motivating detect-then-verify. \emph{Position:} we use
negative-cycle detection strictly as a candidate generator, never the profit oracle.

\subsection{Convex routing and optimal sizing}
For a two-pool $x\cdot y=k$ cycle the optimal input is a closed form (collapse two
hops, solve $dP/dx=0$), implemented in \code{strategy/arb.go} with integer
floor-sqrt. For multi-hop/split routing, convex optimization over CFMMs is the
principled framework: concavity of trading functions \cite{angeris2020oracles},
multi-asset convex programs \cite{angeris2021multiasset}, the canonical routing
program where arbitrage is the special case \cite{angeris2022routing}, and the dual
decomposition into per-market arbitrage subproblems \cite{diamandis2023routing},
generalized to convex flows over hypergraphs \cite{diamandis2024convexflows}.
\emph{Position:} closed form for isolated V2 cycles, dual-decomposition for
coupled/split, and for V3 we let the EVM size the trade (golden-section over Quoter
evaluations), exact where no closed form exists.

\subsection{Concentrated liquidity (V3)}
\emph{Uniswap v3 Core} \cite{adams2021uniswapv3} bounds liquidity to price ranges;
$x\cdot y=k$ breaks because $L$ is piecewise-constant across ticks, and exact output
is a tick-by-tick iteration with no single closed-form optimum. \emph{Position:} we
use \code{slot0.sqrtPriceX96} only as a candidate detector and \emph{never} compute
V3 profit analytically---we defer to the EVM (QuoterV2 / pool bytecode), strictly
more accurate than any re-implementation and already receipt-validated.

\subsection{Flash loans and capital-free execution}
Qin et al.\ \cite{qin2021flashloans} formalize flash-loan search over chain state.
Flash swaps / flash loans reduce required inventory to $\sim$0, so the binding
constraints become gas $+$ builder bid (plus a flash premium for Aave).
\emph{Position:} we assume flash funding, $\text{net} = \text{gross} - \text{gas} -
\text{bid} (- \text{flashPremium})$; V2 in-kind premium is $0$ (our default).

\subsection{Sandwich attacks: formalization and concentrated-liquidity profitability}
Where cyclic/backrun arbitrage exploits a \emph{pre-existing} cross-venue
discrepancy, a \textbf{sandwich} \emph{manufactures} the discrepancy by front- and
back-running a victim swap in the same pool. Zhou et al., \emph{High-Frequency
Trading on Decentralized On-Chain Exchanges} \cite{zhou2021hft}, were the first to
formalize and quantify sandwiching, deriving the optimal frontrun size for a
constant-product pool and showing a single adversary could earn thousands of USD/day
on Uniswap. Qin et al.\ \cite{qin2022quantifying} subsequently folded sandwiching
into their chain-wide extractable-value census alongside arbitrage and liquidations,
and the front-running measurement of Torres et al.\ \cite{torres2021frontrunner}
situates it in the broader transaction-ordering threat surface systematized by
Heimbach and Wattenhofer \cite{heimbach2022sok}.

The constant-product optimal-frontrun closed form does not survive contact with
concentrated liquidity. Gogol et al.\ \cite{gogol2026sandwich} develop an
attacker-profitability model for both CPMMs and concentrated-liquidity AMMs
(Uniswap/Pancake v3) and derive the corresponding optimal strategy, confirming that
the V3 sandwich optimum is not a single closed form because effective liquidity is
piecewise-constant across ticks---the same obstacle we hit for V3 \emph{backrun}
sizing and resolve the same way: we use the closed form only to \emph{seed} a search
whose every probe is a ground-truth EVM evaluation of the full three-leg
construction (\S\ref{sec:sandwich-method}), so V3 sandwich profit is priced by the
pool's own \code{TickMath}/\code{SwapMath} rather than any analytic surrogate.
\emph{Position:} sandwiching is the dominant atomic MEV category on BSC by
value---roughly half of measured BSC MEV---yet the empirical-measurement literature
prices it analytically or by log heuristics (e.g.\ the large-scale post-Merge
Ethereum remeasurement of Chi et al.\ \cite{chi2024remeasuring}, $\sim$3M sandwiches
detected by pattern rules rather than re-execution), inheriting the V3 and revert
mis-pricing we set out to eliminate; the one close non-analytic precedent, Lanturn
\cite{babel2023lanturn}, EVM-simulates sandwiches but per chosen target, not as a
per-block census. We contribute the first (to our knowledge) \emph{receipt-exact,
EVM-constructed} per-block census of the sandwich opportunity surface available to an
independent searcher on post-PBS BSC, on the \textbf{same instrument and the same
victim stream} as our backrun measurement---making the two directly comparable and
turning ``which atomic strategy actually has an edge?'' from an apples-to-oranges
literature comparison into a single controlled experiment.

\subsection{The BSC PBS regime (BEP-322)}
BSC adopted PBS via BEP-322 \cite{bep322}: Builder API, no relay, whitelisted
builders, private flow ahead of the mempool. Wang et al.\ \cite{wang2025binance}
measure that two builders produce most blocks and capture most MEV, the dominant
strategy is short hub cycles, opportunities live $\sim$100--400\,ms, and path length
barely correlates with profit. \emph{Position:} this explains our null on the major
hub pools and points residual edge (if any) to longer/cross-DEX/V3 and long-tail
cycles---scoped in \S\ref{sec:discussion}.

\subsection{Summary of what we adopt vs.\ scope out}
\begin{table}[h]\centering
\caption{What we adopt vs.\ scope out from prior work.}\label{tab:adopt}
\small
\begin{tabular}{p{4.3cm}p{2.6cm}p{3.2cm}p{2.6cm}}
\toprule
Technique & Source & We use it as & Adopt / Scope-out \\
\midrule
Negative-cycle (Bellman--Ford/SPFA) on $-\ln(r(1-\text{fee}))$ & classical;
  \cite{wang2021cyclic} & candidate generator only & \textbf{Adopt} \\
Line-graph $+$ Modified MBF & \cite{zhang2024improved} & many-cycle enumeration &
  \textbf{Adopt (optional path)} \\
Two-pool closed-form optimal input & UniswapV2; \code{arb.go} & exact V2 sizer &
  \textbf{Adopt (implemented)} \\
Convex optimal routing & \cite{angeris2022routing} & multi-path/cross-DEX sizing &
  \textbf{Adopt for coupled cycles} \\
Dual decomposition / per-CFMM oracle & \cite{diamandis2023routing} &
  implementable multi-pool engine & \textbf{Adopt for coupled/split} \\
Convex network flows (hypergraph) & \cite{diamandis2024convexflows} & most-general
  split routing & \textbf{Scope-out (future)} \\
V3 tick math & \cite{adams2021uniswapv3} & spot-price candidate detector only &
  \textbf{Adopt detector; defer profit to EVM} \\
Detect-then-EVM-value & this work; \cite{mclaughlin2023arbitrage} & core methodology
  & \textbf{Adopt (our contribution)} \\
Flash swaps / flash loans & \cite{qin2021flashloans} & capital-free cost model &
  \textbf{Adopt (assumption)} \\
Sandwich formalization $+$ CP optimal frontrun & \cite{zhou2021hft} & seed sizer;
  victim-impact model & \textbf{Adopt; profit deferred to EVM} \\
V3/CLMM sandwich profitability & \cite{gogol2026sandwich} & confirms no V3 closed
  form & \textbf{Adopt detector; defer profit to EVM} \\
BSC PBS reality & \cite{bep322,wang2025binance} & regime framing for the null &
  \textbf{Adopt (interpretation)} \\
Adaptive-learning executing MEV optimizer & \cite{babel2023lanturn} & nearest
  non-analytic prior art (per-target executor) & \textbf{Contrast (per-block census
  vs.\ per-target optimizer)} \\
Heuristic arbitrage$+$sandwich remeasurement & \cite{chi2024remeasuring} & recent
  large-scale measurement comparator & \textbf{Contrast (detection vs.\
  re-execution)} \\
\bottomrule
\end{tabular}
\end{table}

% ===========================================================================
\section{Methodology}

\subsection{Node substrate}
A single bsc-geth v1.7.3 full node (PBSS state, snapshot-seeded, 64-core/125\,GB),
synced to BSC mainnet ($\text{chainId}=56$, head $\sim$block 102.54M). Stock
v1.7.3 plus read-only instrumentation (\code{simengine}, \code{strategy}, a disarmed
Phase-3 \code{builder}/\code{wallet}/\code{contracts}); built with
\code{GOTOOLCHAIN=auto} only to \code{/tmp/geth-sim10}. Every on-chain
constant---addresses, V2 slot 8 packing, V3 \code{slot0} layout, fee tiers,
decimals, reserves, selectors---was verified directly against this node, the same
state source the SimEngine executes on.

\subsection{The SimEngine}
\code{simengine/simengine.go} speculatively executes a tx list on a copy of
canonical state, mirroring \code{core.StateProcessor.Process} and the miner worker
but never committing: switch to \code{statedb.Copy()}; apply system-contract upgrades
keyed off \emph{parent} block time; seed the gas pool from \code{header.GasLimit}
minus Parlia reserved gas; build the EVM with the header coinbase as author; run
pre-execution system calls; iterate txs, \emph{skipping Parlia system transactions}
(they run in \code{Finalize}), with per-tx snapshot/revert on error; return
receipts, flattened execution-ordered logs, gas, and balance deltas. The single loop
\code{applyOnState} is shared by the self-test and the backtest, so validation and
measurement are byte-for-byte the same code. Running the actual pool bytecode handles
V3 tick-crossing, stableswap, fee-on-transfer, hooks, slippage reverts, and rounding
exactly---an analytic study must model each, and any divergence is a silent error;
we have none by construction.

\subsection{Validation against stored receipts (5/5 PASS)}
\label{sec:validation}
\code{simengine/selftest.go} replays real blocks and compares simulated receipts to
the stored receipts by tx hash over \textbf{Status, GasUsed, CumulativeGasUsed} and
every log's \textbf{Address, Topics, Data}. Result: \textbf{5/5 PASS} on blocks
around height 101.83M, 100--151 txs each, no field mismatch on any tx
(Table~\ref{tab:val}). Matching every log and gas figure across 100+ txs on copied
state is an extremely tight constraint that implicitly exercises the post-state root.

\paragraph{Phase-2 widened validation (500 stratified blocks).} Per the revision plan
we widened this certificate from a 5-block cluster to a 500-block stratified sample
drawn from a $9{,}989$-block forward-from-head window (stride $20$, heights
$\sim$$102{,}991{,}477..103{,}001{,}466$). Result on the widened sample:
\textbf{passRate}$=1.00$, \textbf{passed}$=500$, \textbf{failed}$=0$, droppedTxBlocks$=0$
over totalTxs$=47{,}586$, failedTxs$=0$; the stratification covers V3-heavy blocks
(v3Blocks$=455$) and fee-on-transfer pools (fotBlocks$=42$); all mismatch counters are
$0$. This replaces the ``n$=$5 cluster-localized'' smoke test with a measured,
stratified validation in the actual measurement height range, on this window.

\subsection{Backtest protocol}
\code{simengine/dryrun.go} is read-only and crash-safe (\code{defer/recover};
no-op unless \code{SIMENGINE\_DRYRUN} is set; never submits). Per imported head it
re-executes the whole block on a \code{state.Copy()} of the parent. Three modes:
\emph{backtest} and \emph{graph} (post-block, v1/v2; evaluate the boundary---not a
valid backrun test, \S\ref{sec:postblock}); \emph{intrablock} (v3/v4; the correct
test) hooks in after each watched-pool \code{Swap}, snapshots reserves there, builds
the graph, enumerates cycles $2..K$ from WBNB, and values each (V2 closed form; V3
via the EVM oracle). Funnel counters and the distribution accumulator are tallied
per processed block and logged on the \code{TallyEvery} cadence. Reserves: V2 slot 8
holds packed $(\text{reserve0},\text{reserve1},\text{ts})$; V3 \code{slot0} holds
\code{sqrtPriceX96} (low 160 bits) and \code{tick}, spot $P=(\text{sqrtPriceX96}/2^{96})^2$.
A disarmed Phase-3 submitter exists only to make the realizability discussion
concrete; it is not used for any measurement.

\subsection{The EVM valuation oracle (Stage B)}
\label{sec:oracle}
For each candidate the oracle chains hop outputs into hop inputs on the exact
intermediate \code{state.Copy()}: V2 hops by the exact closed form (which the
self-test validates to receipt level for real V2 swaps); V3 hops by a read-only,
\code{Snapshot}/\code{Revert}-bracketed EVM call (\code{simengine/evmcall.go},
\code{EthCall}) to PancakeSwap \emph{QuoterV2}
(\code{0xB048Bbc1...25997}, selector \code{0xc6a5026a}), which reverts-to-return the
exact output the pool would produce. Optimal input is found by golden-section
(\code{strategy/quoter\_oracle.go}) whose every probe is an EVM evaluation;
per-cycle gas is \code{CycleGasUnits(cycle)} ($\sim$280k). $\text{net}=\text{gross}-
\code{CycleGasUnits}\cdot\text{gasPrice}-\text{bid}-\text{margin}$. This is the
\emph{sole} profit authority; no profit is ever taken from Stage~A.

\subsection{Metrics}
Coverage (blocks processed, sampling fraction); the candidate funnel (Stage-A
candidates, EVM gross-positive, net-positive); the gross-profit distribution (USD
percentiles + exact max); the break-even gas-price distribution (gwei); a
$\{0,0.1,0.3,1,3\}$ gwei sensitivity sweep; and the structural breakdown by DEX mix
and cycle length. The Stage-A$\to$Stage-B and gross$\to$net ratios give RQ3. For
sandwiching (\S\ref{sec:sandwich-method}) we report the analogous funnel---victims
seen, fundable, supported, above-threshold, gross-positive, net-positive---plus the
same gross-profit distribution, break-even gas, and gas-sweep, all denominated in
BNB.

\subsection{Sandwiching: ground-truth construction and valuation}
\label{sec:sandwich-method}
Backrun arbitrage is \emph{parasite-free}: the searcher inserts one transaction
after a victim swap and the victim is unaffected. A \textbf{sandwich} is adversarial
and three-legged: the attacker (1)~\textbf{frontruns}---buys the same direction as
the victim, worsening the victim's execution price; (2)~lets the \textbf{victim}
execute at the degraded price; (3)~\textbf{backruns}---sells the position back into
the pool the victim just pushed, realizing the spread the attacker manufactured.
Unlike backrun arbitrage, sandwich profit is \emph{created} by the attacker's own
frontrun, so it cannot be read off pool reserves analytically without re-deriving
the full three-trade price path---and on real pools that path includes V3
tick-crossing, fee-on-transfer tokens, and reverts that closed-form CFMM math
silently mis-prices \cite{zhou2021hft,gogol2026sandwich}. This is exactly where the
SimEngine's receipt-exact substrate pays off a second time: we \emph{construct} the
sandwich and let the EVM price it. Caveat: the real-block replay is receipt-validated
(\S\ref{sec:validation}), but the counterfactual sandwich construction is not
receipt-validated against a real landed sandwich (no ground truth exists); the
construction is argued to be conservative but this is a key limitation for exotic long-tail
tokens (T12).

\subsubsection{The construction}
For each victim swap surfaced by the intra-block trigger (\S\ref{sec:models-sandwich})
we build a synthetic 3-tx sequence on a fresh \code{parent.Copy()} and re-execute it
with the same \code{core.ApplyTransaction} / in-process \code{vm.Call} machinery
validated in \S\ref{sec:validation}:
\begin{enumerate}
  \item \textbf{Fund a synthetic attacker.} A throwaway attacker address is given
    inventory of the pool's \emph{numeraire} token (\S\ref{sec:numeraire}) by writing
    the ERC20 balance and allowance storage slots directly on the copied
    state---never on canonical state. For the hub tokens the slots are known and
    hardcoded (WBNB balance slot 3 / allowance slot 4; USDT, USDC balance slot 1 /
    allowance slot 2). For arbitrary long-tail tokens we \textbf{probe the layout at
    runtime}: we write a sentinel to candidate \code{keccak256(addr . slot)} mappings
    for $\text{slot}\in\{0..12\}$, call \code{balanceOf(addr)} through the EVM, and
    accept the first slot whose read returns the sentinel (cached per token). Tokens
    whose \code{balanceOf} cannot be reproduced by any standard mapping slot
    (proxies, exotic layouts) are counted \code{skippedUnfundable} and excluded---a
    \emph{conservative} exclusion that can only \emph{lower} the measured sandwich
    count.
  \item \textbf{Frontrun.} The attacker swaps an optimally-sized amount of numeraire
    into the victim's direction, \emph{on the victim's actual pool}. Routing matters:
    we do not assume a fixed router. V2-family pools (Pancake V2 and any $x\cdot y=k$
    fork---Biswap, ApeSwap, \dots) are swapped by encoding a \textbf{direct
    \code{pair.swap(amount0Out, amount1Out, to, data)}} (selector \code{0x022c0d9f})
    with a K-safe \code{amountOut}: we compute the output with the \emph{Pancake}
    $0.25\%$ fee even when the fork's true fee is lower, which \emph{under-quotes} the
    attacker's output and so never over-states sandwich profit on a fork we have not
    fee-calibrated. Pancake V3 pools are swapped through the real Pancake V3
    \code{SwapRouter} (\code{0x1b81D678...213eB14}, \code{exactInputSingle} with the
    deadline-bearing selector \code{0x414bf389}). Non-Pancake V3 / Algebra pools we do
    not yet route and count \code{skippedUnsupported}.
  \item \textbf{Victim.} The victim's \emph{real} transaction is replayed verbatim on
    the post-frontrun state (no snapshot/revert bracketing---\S\ref{sec:evmfixes}), so
    the victim executes against exactly the reserves the attacker's frontrun left
    behind, with the EVM applying every slippage guard the victim's own calldata
    carries (a sandwich that would trip the victim's \code{amountOutMin} simply yields
    a revert and zero profit, caught for free).
  \item \textbf{Backrun.} The attacker swaps its entire acquired position back through
    the same pool, again via the K-safe direct path, closing the loop.
\end{enumerate}
The attacker's \textbf{gross} is the change in its numeraire balance across the three
legs, read from the copied \code{StateDB}---the EVM's own number, inclusive of all
three real swaps' fees, tick crossings, and rounding. No CFMM closed form is used to
\emph{value} the sandwich; the closed form (\S\ref{sec:models-sandwich},
\code{strategy/sandwich.go}) is used \emph{only} to seed the optimal-frontrun search.

\subsubsection{Optimal frontrun size}
The frontrun size trades off manufactured spread against the attacker's own price
impact: too small and the victim is barely moved, too large and the attacker pays
more slippage on entry/exit than it extracts. We seed with the V2 closed-form
sandwich optimum ($\gamma$-parameterized, \code{strategy/sandwich.go}) and refine by
evaluating candidate sizes through the full EVM construction above, capping the
frontrun at $\leq$100\% of the victim's input notional and $\leq$50\% of the pool's
numeraire reserve (a liquidity-sanity bound that prevents the optimizer from
proposing a frontrun the pool could not absorb without absurd impact). The reported
gross is the EVM value at the best feasible size.

\subsubsection{Denomination in a single numeraire (and an integrity catch)}
\label{sec:numeraire}
A sandwich's three legs move two tokens; profit must be reported in \textbf{one}
unit. Our first any-pool implementation contained a \textbf{units bug} worth
recording because it shaped the protocol: it measured the attacker's gross in
whatever token the victim happened to \emph{spend} (often an arbitrary memecoin)
while subtracting the gas cost in BNB. Mixing a memecoin-denominated gross with a
BNB-denominated cost made the net gate meaningless and produced absurd aggregates (a
total ``net'' of order $10^{30}$ wei---$\sim$$10^{12}$ BNB---and an implied
break-even gas price of $\sim$$10^{9}$ gwei). The figures were \emph{flagged as
not-real on sight} and never reported; the bug was the detector's, not the chain's.

The fix defines, for each victim pool, a \textbf{numeraire}---the side that is a hub
asset with a known BNB price (WBNB directly; USDT/USDC via the WBNB/stable pool). The
synthetic attacker is funded \emph{in the numeraire}, both swap legs are denominated
in the numeraire, and gross/net/gas/flash-fee are all expressed in BNB. Pools with
\textbf{no} hub-asset side (pure token/token pairs) cannot be denominated and are
counted \code{skippedNoNumeraire} and excluded. This both fixes the accounting and
scopes the measurement to economically interpretable opportunities. After the fix the
same sample produced realistic magnitudes (per-sandwich net of order $10^{-4}$--$10^{-2}$
BNB, aggregate tens of BNB, break-even gas in the single-to-hundreds-of-gwei range)
---sanity-checked against the published BSC sandwich-MEV figure before being trusted
(\S\ref{sec:extval}). We document this bug for reproducibility.

\subsubsection{EVM-mechanics fixes}
\label{sec:evmfixes}
Constructing multi-leg synthetic transactions on copied state surfaced three EVM
state-management subtleties, each fixed and unit-tested:
\begin{itemize}
  \item \textbf{``revision id N cannot be reverted.''} Bracketing a
    \code{core.ApplyTransaction} in an outer \code{Snapshot}/\code{RevertToSnapshot}
    is illegal because \code{ApplyTransaction}'s own \code{Finalise} clears the
    journal's valid revisions. We removed the outer snapshot/revert and obtain
    isolation purely from a fresh \code{parent.Copy()} per sandwich probe (each probe
    is independent by construction).
  \item \textbf{``Refund counter below zero ($\text{gas}>\text{refund}:0$).''} A
    read-only \code{vm.Call} leg (the V3 router) inherits a stale refund counter. We
    wrap each EVM leg with \code{statedb.Prepare(rules, attacker, coinbase, \&router,
    ActivePrecompiles, nil)} before and \code{statedb.Finalise(true)} after, mirroring
    the canonical per-tx lifecycle so the refund accounting is well-formed.
  \item \textbf{Wrong-router routing.} An early version hardcoded the attacker to a
    Pancake router regardless of the victim pool, mispricing fork pools. The K-safe
    direct \code{pair.swap} to the victim's \emph{actual} pool removes the assumption.
\end{itemize}

\subsubsection{Cost gate}
$\text{net}=\text{grossBNB}-\text{gasBNB}-\text{flashFeeBNB}$. Gas is the measured
3-leg cost (frontrun $+$ backrun; the victim's gas is the victim's, not the
attacker's) at the swept gas prices; the attacker is assumed flash-funded so the only
capital cost is the flash premium on the numeraire borrowed for the frontrun
(\code{flashFeeBNB}, V2 in-kind $\approx 0$, Aave-style a few bps). As with backrun,
every assumption is generous to the attacker, so the reported net-positive sandwich
count is an \emph{upper bound}.

\subsection{The in-block counterfactual: ex-post existence vs.\ realized capture}
\label{sec:counterfactual}
Everything to this point measures \emph{ex-post existence}---that an opportunity was
present on-chain. The decision-relevant quantity is \emph{realizable capture}: how
much an independent searcher could actually take. The gap between them is exactly what
an integrated, latency-advantaged competitor removes. We measure that gap directly, on
the same ground-truth substrate, with an \textbf{in-block counterfactual}: for each
ex-post opportunity our detector surfaces in a canonical block, we ask whether a
\emph{real} competitor already captured it \emph{in that same block}. Captured
$\Rightarrow$ unavailable; uncaptured $\Rightarrow$ ``left on the table'' (still an
upper bound---see \S\ref{sec:realizable}).

\subsubsection{Detecting a landed sandwich in the canonical block}
The detector mode \code{SIMENGINE\_DRYRUN=realizability} rides on the \emph{same
single} \code{ApplyOnStateHooked} replay used everywhere else (no extra EVM execution,
no mutation of canonical state). In one pass it (a)~runs the unchanged ex-post
sandwich-any evaluation (\S\ref{sec:sandwich-method}) to enumerate the block's ex-post
net-positive opportunities, and (b)~builds a per-transaction ledger of hub-asset
balance deltas and parses every V2/V3 \code{Swap} log into legs
\code{(pool, txIdx, direction, sender, beneficiary, from-EOA, amounts)}. It then
declares a \textbf{landed sandwich} on a pool only when a \emph{conjunction} of strong
signals holds---the design is deliberately biased so that, under any doubt, an
opportunity falls to \emph{left-on-the-table} rather than \emph{captured}
(over-counting capture would understate the realizable surface, the dangerous
direction):
\begin{enumerate}
  \item \textbf{Bracket structure.} A front leg and a back leg on the \emph{same
    pool}, in \emph{different} transactions with the victim between them, in
    \emph{opposite} directions. JIT liquidity (Mint/Burn around the swap) is excluded.
  \item \textbf{Same actor.} The two legs share a discriminating actor: the \emph{same
    signing EOA} sent both bracket transactions
    ($\text{from}_{\text{front}}=\text{from}_{\text{back}}$---the strongest real-bot
    signal, since searchers route through their own contract but pay from one EOA), or
    a shared \code{Swap} sender/beneficiary that is neither a known router/aggregator
    nor the block coinbase.
  \item \textbf{Profit corroboration (the false-positive guard).} The bracket must be
    a genuine round trip: net-\emph{flat} in the volatile token and net-\emph{positive}
    in the hub asset on \emph{that pool}, net of gas and any coinbase bribe, above a
    USD dust floor. Hub profit is read over the actor's address \emph{cluster}
    (signing EOA plus the legs' contract sender/beneficiary, minus routers/coinbase),
    because a real bot pays gas from its EOA while the proceeds accrue to its contract.
    A coincidental router routing two unrelated swaps fails this gate.
\end{enumerate}
Captured opportunities are attributed to a \textbf{builder} (block coinbase / a
builder contract registry), a \textbf{repeated MEV sender} (clustered across blocks),
or \textbf{unknown}. The mode emits a \code{realizability tally} (ex-post, captured,
left-on-table, capture rate, attribution) and a \code{realizability dist} (BNB
distributions of captured vs left), plus the funnel counters of the next paragraph.

\subsubsection{An integrity episode (recall failure), and why the funnel is reported}
The first implementation of this detector reported \code{captureRate = 0.00}---\emph{zero}
captured across hundreds of blocks. We did \textbf{not} report it: a zero capture rate
is implausible given the literature on integrated BSC sandwichers, and an
implausible-good result is exactly what the ground-truth discipline
(\S\ref{sec:numeraire}) exists to catch---this time in the \emph{opposite} direction
(a false \emph{zero} rather than a false \emph{fortune}). The cause was a recall bug:
the same-actor gate required the shared \code{Swap}-log actor to equal a leg's signing
EOA, but real bots' \code{Swap} actor is their \emph{contract}, never the EOA, so every
bracket was dropped before corroboration. The fix (the
$\text{from}_{\text{front}}=\text{from}_{\text{back}}$ signal plus cluster-based
hub-profit corroboration) was verified by a unit test of precisely the integrated-bot
pattern (contract actor, single signing EOA, profit in the contract) and by an
independent, pool-agnostic scan of $1{,}500$+ canonical blocks. To make any future
near-zero \emph{auditable} rather than blind, the detector permanently emits the funnel
\code{bracketCandidates} $\to$ \code{sameActorPass} $\to$ \code{corroboratePass}, with
the corroboration-failure breakdown (\code{notFlat / hubNeg / belowDust}). A near-zero
capture rate is only credible when this funnel shows \emph{why} each candidate
legitimately fails---which \S\ref{sec:realizability} reports.

\subsection{The censorship-differential: the one point-identified extraction estimand}
\label{sec:censorship-method}
The realizability counterfactual (\S\ref{sec:counterfactual}) measures whether an
ex-post opportunity was captured \emph{in the block}. It does not, by itself, isolate
the value an independent could \emph{reach}. The naive ``predicted-vs-sealed'' contrast
for total builder MEV is \textbf{non-identified}: private order flow is a \emph{selected}
treatment (correlated with state via routing) and per-transaction value depends on the
whole ordering, so SUTVA fails. The one estimand that survives this is the
\textbf{censorship-differential}
\begin{equation}
D = \mathbb{E}\big[\,V_i(1)-V_i(0)\ \big|\ o_i\ \text{public},\ o_i\perp\ \text{private flow},\ \text{builder dropped } o_i\,\big],
\end{equation}
the receipt-exact value a builder leaves on the table by \emph{dropping} (rather than
including or internalizing) public, private-flow-orthogonal opportunities---the slice an
independent party can, in principle, structurally reach. Measuring $D$ adds one data
dimension the rest of the paper lacks: the \textbf{public mempool}, which supplies the
treatment assignment (a public opportunity was included vs dropped).

\subsubsection{Construction (\code{SIMENGINE\_DRYRUN=censorship})}
The detector runs \emph{live}, ingesting the public mempool via a
\code{SubscribeTransactions} goroutine into a rolling, sender/nonce-indexed ledger
(first-seen timestamp per hash). Per sealed block it builds inclusion/replacement
indices from the canonical txs, runs one hooked replay to obtain the
\textbf{post-sealed-block state}, and applies a conjunction of gates to every public
candidate---every one biased so that \emph{ambiguity excludes} (over-stating $D$ is the
dangerous direction; $\hat D$ is a strict lower bound):
\begin{enumerate}
  \item \textbf{Available-at-seal}---recovered, correct-nonce
    (\code{GetNonce==tx.nonce}), valid and funded on the sealing parent; not
    nonce-gapped.
  \item \textbf{Dropped, not replaced}---its \code{(sender,nonce)} slot is not filled by
    a different hash in the block.
  \item \textbf{Net-of-gas profitable, self-contained}---valued by re-executing the
    candidate \textbf{alone on the post-sealed-block state} (\S\ref{sec:censorship-val}),
    reading the executor's own BNB-denominated hub-asset delta net of gas; must emit
    $\geq$2 directional Swap legs (a single one-way swap's positive hub delta is sale
    proceeds, not profit) and clear a USD dust floor.
  \item \textbf{Orthogonal to private flow}---no other sealed tx touches the opportunity
    pool (the SUTVA gate).
  \item \textbf{Settled-never-mined} (\S\ref{sec:settle-window})---the decisive gate.
\end{enumerate}

\subsubsection{Valuation on the post-block state (integrity episode 3)}
\label{sec:censorship-val}
A first implementation valued the candidate as the profit of \emph{sandwiching} it---the
\textbf{inverse} of $D$ (a sandwich-the-user surface that over-states $D$ by
construction); caught in adversarial review and rewritten to the candidate's \emph{own}
realized net profit. A second version valued that own profit on the \emph{pre-seal
parent} state, in isolation---which counts opportunities the realized block had already
closed (including by the builder's own internalized arb). We re-value on the
\textbf{post-sealed-block state}: a candidate counts only if it is still profitable
\emph{after the entire builder block has executed}. This is conservative (it may
under-state $D$: an opportunity profitable mid-block but closed by block-end is
excluded) and it subsumes builder self-internalization for free (the internalizing tx is
in the post-block state).

\subsubsection{The settle window (integrity episode 4)}
\label{sec:settle-window}
The load-bearing definition is ``dropped''. Defining it as ``absent from \emph{this}
block'' conflates \emph{censored} with merely \emph{pending}. We add a \textbf{settle
window} of $K$ blocks (default 256): a candidate is credited to $D$ only if, after $K$
subsequent blocks, its hash is \emph{still absent from the canonical chain} (checked
against a rolling mined-hash index; sender-nonce-advanced candidates are discarded as
superseded). A candidate mined within the window is \emph{delayed inclusion}, not
censorship, and becomes an \code{includedComparable} control (the $T=1$ arm). The
detector defers the credit decision, freezing $V_i$ at flag time and finalizing $K$
blocks later. This is the gate that makes $\hat D$ a defensible lower bound rather than a
count of pending transactions.

These two episodes join the units-bug (\S\ref{sec:numeraire}), the realizability
recall-bug (\S\ref{sec:counterfactual}), and the backrun-any decimal-mismatch
sanity-cap fire (catch~\#5: \S\ref{sec:contrast} / \S\ref{sec:threats}; sanity-cap
fired 4$\times$ on block 103{,}005{,}219---a BUSD$\to$WBNB$\to$BUSD 2-hop V2 whose
CycleOptimum returned grossUSD $\sim$$3.6\times10^{15}$ from a V2 decimal-mismatch on
a high-decimal memecoin pool; caught-not-baked via the \$100k$/$1000~BNB sanity-cap
and the \code{brSkippedSanityOutlier} counter, with REJECT log): in total we found
and fixed \textbf{five integrity catches} in the detectors during development,
documented here for reproducibility. The discipline is reproducible---this is the
fifth catch confirming the measurement-integrity protocol.

% ===========================================================================
\section{Models: Naive Baseline to EVM Oracle}

\subsection{Naive baseline (v1)}
Three deep all-18-decimal Pancake V2 pairs (WBNB/USDT, WBNB/USDC, USDT/USDC), fee
$0.25\%$ ($\gamma=9975/10000$). Exact integer single-hop output; sqrt-free gate
$\gamma_{\text{num}}^2 R_{aO} R_{bO} > \gamma_{\text{den}}^2 R_{aI} R_{bI}$;
closed-form optimal input via integer floor-sqrt (unit-tested to exact wei);
$\text{net}=\text{gross}-\text{gas}-\text{bid}-\text{margin}$ with 250k gas, 3\,gwei,
bid $0$, margin $0$. Detection by a router-agnostic post-block \code{Swap}/\code{Sync}
log scan. Result: \textbf{$0/5{,}100$ blocks, $0$ would-be profit}. Limits removed
later: only 2-pool cycles among 3 hardcoded pools; only $x\cdot y=k$; post-block;
analytic valuation.

\subsection{Cross-DEX V2 graph (v2)}
A token multigraph with edges carrying pool/DEX/$\gamma$, marginal rate, and weight
$-\ln(r(1-\text{fee}))$ (detection only; valuation in \code{big.Int}).
\code{NegativeCycles} enumerates cycles $2..K$ from WBNB; isolated all-V2 cycles are
sized by the exact linear-fractional hop composition $f(x)=ax/(b+cx)$,
$x^\ast=(\sqrt{ab}-b)/c$ (the exact generalization of the 2-pool optimum). Adding
three Biswap V2 pools (fee $0.20\%$) yields 6 V2 pools and cross-DEX cycles. Result:
\textbf{$0$ Stage-A candidates $/2{,}950$ blocks} (snapshot spreads $0.029\%/0.078\%
\ll 0.45\%$ fee threshold). Still post-block.

\subsection{Intra-block detector (v3, v3+V3)}
The correct trigger: after each transaction emitting a watched-pool \code{Swap} (V2
\code{Swap}/\code{Sync} plus the V3 \code{Swap} topic \code{0xc42079f9...}), snapshot
reserves there and run the negative-cycle finder. V2-only: \textbf{$0$ candidates}
(V2 pools quiet). Adding six Pancake V3 pools (read via \code{ReadSlot0}/
\code{V3SpotPrice}) surfaces \textbf{$803$ Stage-A candidates $/3{,}000$ sampled
blocks}, \emph{detected but unvalued} ($\code{CycleOptimum}=(0,0)$ for V3
cycles)---the Stage-A/Stage-B split that justifies the oracle.

\subsection{EVM oracle (v4) and cost / PBS model}
Stage~B (\S\ref{sec:oracle}) values every candidate exactly. $\text{net}=\text{gross}
-\code{CycleGasUnits}\cdot\text{gasPrice}-\text{bid}$, capital-free flash funding
\cite{qin2021flashloans}, bid $0$ in the headline (most generous). We emit the
gross-profit distribution, break-even gas price, and the $\{0,0.1,0.3,1,3\}$ gwei
sweep (\code{strategy/distribution.go}). \textbf{Realizable vs.\ ex-post (central
caveat):} the backtest measures ex-post would-be gross against the post-swap
transient; under BSC PBS \cite{bep322,wang2025binance} a positive figure is an
\emph{upper bound} on realizable profit, so the thin ex-post net-positive residual
we report ($15$ of $803$) is an upper bound on what an independent searcher could
realize, not a capture claim---that above-gas tail is the slice builders take first.

\subsection{Sandwich model (any-pool)}
\label{sec:models-sandwich}
The sandwich model reuses the exact same intra-block trigger as v4---every
watched-pool victim swap---but, instead of searching for a trailing cross-venue
cycle, it constructs and EVM-values the three-leg attack of \S\ref{sec:sandwich-method}
on the victim's own pool. Two design choices make it a \emph{long-tail} instrument
rather than a hub one:
\begin{enumerate}
  \item \textbf{Any-pool decode.} A victim is any transaction emitting a V2 \code{Swap}
    (\code{0xd78ad95f...}) or V3 \code{Swap} (\code{0xc42079f9...}) on \emph{any} pool,
    not only the verified 12-pool watch set---so the model sees the memecoin/WBNB long
    tail where sandwiching actually concentrates. Pool metadata
    (token0/token1, reserves, fee family) is read from the runtime state of whatever
    pool emitted the event.
  \item \textbf{Numeraire gate (\S\ref{sec:numeraire}).} Only pools with a hub-asset
    side (WBNB or a major stable) are valued, in BNB; pure token/token pools are
    \code{skippedNoNumeraire}.
\end{enumerate}
The sizer is the $\gamma$-parameterized V2 sandwich closed form
(\code{strategy/sandwich.go}) used \emph{only} to seed; the profit authority is the
EVM construction. $\text{net}=\text{grossBNB}-\text{gasBNB}-\text{flashFeeBNB}$, with
the same $\{0,0.1,0.3,1,3\}$ gwei sweep. The funnel counters (\code{victimsSeen},
\code{skippedUnfundable}, \code{skippedUnsupported}, \code{skippedNoNumeraire},
\code{belowThreshold}, \code{grossPositive}, \code{netPositive}, \code{totalNetWei})
and the BNB-denominated distribution accumulator are tallied per processed block
exactly as for backrun, so the two strategies are reported on identical scaffolding.

% ===========================================================================
\section{Results}

All figures are produced by the read-only backtest harness on the synced bsc-geth
v1.7.3 node, with the receipt-validated SimEngine as the profit oracle. The
\textbf{backrun} experiments (\S\ref{sec:backrun-results}) run with
\code{SIMENGINE\_DRYRUN=intrablock}; the \textbf{sandwich} experiments
(\S\ref{sec:sandwich-results}) run with \code{SIMENGINE\_DRYRUN=sandwich-any}; both
take \code{SIMENGINE\_DRYRUN\_TALLY=N} and
\code{SIMENGINE\_DRYRUN\_GASPRICES="0,0.1,0.3,1,3"}. Everything is strictly
read-only; nothing is submitted; node/systemd/datadir are untouched; the binaries are
built only to \code{/tmp} (\code{geth-sim10} for backrun, \code{geth-sim15} for the
numeraire-corrected sandwich model). Backrun numbers are from the consolidated
geth-sim10 run ($3{,}000$ sampled blocks; distribution from the last
\code{intrablock dist} line, \S\ref{sec:fill}); sandwich numbers are from the
consolidated geth-sim15 run ($2{,}550$ sampled blocks; funnel and distribution from
the last \code{sandwich-any tally} and \code{sandwich-any dist} lines).

\subsection{SimEngine validation}
\begin{table}[h]\centering
\caption{SimEngine validation against stored receipts.}\label{tab:val}
\begin{tabular}{lll}
\toprule
Metric & Smoke test & \textbf{Phase-2 widened validation} \\
\midrule
Validation method & replay real block & replay forward-from-head, stratified stride-20 \\
Fields compared & Status, GasUsed, etc. & same \\
Blocks validated & 5 ($\sim$101.83M) & \textbf{500 stratified} (9{,}989-block window, heights $\sim$102{,}991{,}477..103{,}001{,}466) \\
Tx per block & 100--151 & totalTxs $=47{,}586$ across the 500 \\
\textbf{PASS / FAIL} & \textbf{5 / 0 (5/5 PASS)} & \textbf{500 / 0 (passRate$=1.00$)} \\
Mismatches & none & none (all counters 0) \\
Coverage & one localized cluster & v3Blocks $=455$, fotBlocks $=42$, droppedTxBlocks $=0$, failedTxs $=0$ \\
\bottomrule
\end{tabular}
\end{table}

\noindent \textbf{Phase-2 widened validation (closes T6).} The original 5-block smoke
test was strong but cluster-localized ($\sim$height 101.83M). Per the revision plan we
widened it to a 500-block stratified sample drawn from a $9{,}989$-block window in the
actual measurement height range ($\sim$103M). The widened sample is \textbf{500/500
PASS} with \textbf{zero mismatches in any field on any tx} across $47{,}586$
transactions, and stratification confirms the oracle handles V3-heavy blocks
(n$=455$) and fee-on-transfer pools (n$=42$) at the same fidelity. T6 (validation
cluster locality) is closed on this window; the protocol scales trivially. ``On this
window'' is meant literally: the certificate is measured on the heights above, not
asserted in general.

\subsection{Model-evolution funnel}
\label{sec:backrun-results}
\begin{table}[h]\centering
\caption{Model-evolution funnel: naive to EVM oracle. All under the same validated
SimEngine substrate.}\label{tab:funnel}
\small
\begin{tabular}{llllrrrr}
\toprule
\# & Model & Scope & Eval.\ point & Range & Stage-A & Gross$+$ & Net$+$ \\
\midrule
v1 & Naive 2-pool & 3 Pancake V2 & post-block & 5{,}100 & --- & --- & \textbf{0} \\
v2 & Graph cross-DEX V2 & 6 V2 & post-block & 2{,}950 & \textbf{0} & 0 & \textbf{0} \\
v3 & Intra-block V2 & 6 V2 & post-swap & (val.\ win.) & \textbf{0} & 0 & \textbf{0} \\
v3+V3 & Intra-block + V3 detect & 12 pools & post-swap & 3{,}000 samp. & \textbf{803} & n/a & n/a \\
v4 & Intra-block + EVM oracle & 12 pools & post-swap & 3{,}000 samp. & \textbf{803} & \textbf{803} & \textbf{15 @ 3 gwei} \\
\bottomrule
\end{tabular}
\end{table}

\noindent v1: $0/5{,}100$, $0$ would-be profit. v2: $0$ candidates $/2{,}950$
(spreads $\ll$ fee threshold---no standing cross-DEX arb). v3: $0$ candidates (major
V2 pools quiet, $\sim$10 Pancake-V2 WBNB/USDT swaps per 30 blocks). v3+V3: $803$
candidates detected but unvalued (V3 closed form intractable). v4: over $3{,}000$
sampled blocks, watchedSwaps $=1{,}554$, Stage-A $=803$, EVM gross-positive
$=803$, net-positive $=15$ at 3 gwei ($1.9\%$)---$\sim$$0.27$ gross-positive
cross-venue cycles per sampled block, $\sim$1 ex-post net-positive per 200 sampled
blocks ($0.017192$ BNB $\approx$ \$10.3 total). These are ex-post figures, not a
realizable-capture claim (\S\ref{sec:realizable}).

\paragraph{Sampling.} The v4 detector samples a representative subset of heads
(per-candidate EVM valuation is slower than block production). Sampling is
incidental, not selective: a uniform-in-time subsample of consecutive heads.
Counters are per processed block; the gross-positive rate is comparable across
windows. The net-positive \emph{rate} is window-sensitive ($0.2\%$ of gross-positive
at the first $600$ sampled blocks vs.\ $1.9\%$ at $3{,}000$), so we headline the
$3{,}000$-block figure and flag the variance.

\subsection{Why post-block evaluation is not a backrun test}
\label{sec:postblock}
The v1/v2 zeros are real but not valid backrun tests. Both evaluate \emph{post-block}
reserves, where cross-venue prices are already re-aligned by intra-block competitors;
backrun MEV lives in the transient state immediately after a victim swap, which
end-of-block evaluation misses. The correct method (v3 onward) hooks in after each
watched-pool swap and values at the only state where a backrun could exist. (The
realizability/race question is separate; \S\ref{sec:realizable}.)

\subsection{Why almost all are sub-gas: gross-profit distribution and gas-sensitivity}
There are $\sim$$0.27$ EVM-confirmed gross-positive cycles per sampled block; the
result is that the overwhelming majority are below the gas cost (at 3 gwei only 15
of 803, $1.9\%$, clear it). From the \code{intrablock dist} log
line (\code{strategy/distribution.go}, $O(1)$ memory: gross-USD and break-even-gwei
in fixed 64-bucket, $0.25$-decade log histograms, so percentiles are bucket
\emph{low edges}---true value in $[\text{edge},\text{edge}\cdot 10^{0.25})$---while
the \code{*\_max} figures are exact running maxima). The gas floor is
$\code{gasUnits}\cdot\text{gasPrice}\approx 280\text{k}\times 3\,\text{gwei}\approx
0.00084\,\text{BNB}\approx \$0.50$.

\begin{table}[h]\centering
\caption{Gross-profit distribution of gross-positive cycles. Percentiles are
log-bucket low edges; max is exact.}\label{tab:gross}
\begin{tabular}{lll}
\toprule
Statistic & Gross (USD) & Relative to \$0.50 \\
\midrule
grossPosSamples (count) & 803 & --- \\
grossUSD p50 & \$0.00056 & $0.0011\times$ \\
grossUSD p90 & \$0.0056 & $0.011\times$ \\
grossUSD p99 & \$1.0 & $2.0\times$ \\
grossUSD max (exact) & \$1.85 & $3.7\times$ \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[h]\centering
\caption{Break-even gas-price distribution. p50/p90 bucketed; max exact.
A cycle is net-positive at price $g$ iff $\text{breakevenGwei}>g$.}\label{tab:break}
\begin{tabular}{lll}
\toprule
Statistic & Break-even (gwei) & vs.\ 3 gwei \\
\midrule
breakevenGwei p50 & 0.0032 & $\sim$1/940 of 3 \\
breakevenGwei p90 & 0.032 & $\sim$1/94 of 3 \\
breakevenGwei max (exact) & 11.1 & $3.7\times$ the 3 gwei price \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[h]\centering
\caption{Gas-price sensitivity sweep: count and \% of gross-positive cycles that
would be net-positive at each price (bid $=$ margin $=0$). At $g=0$ the share is
$100\%$ by definition.}\label{tab:sweep}
\begin{tabular}{lll}
\toprule
Gas price (gwei) & Would-be net$+$ (count) & Share (\%) \\
\midrule
0 & 803 & 100.0 \\
0.1 & 63 & 7.8 \\
0.3 & 45 & 5.6 \\
1 & 29 & 3.6 \\
3 (detector default) & 15 & 1.9 \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[h]\centering
\caption{Structural breakdown of the gross-positive population by DEX mix
(\code{byDexMix}) and cycle length (\code{byCycleLen}).}\label{tab:struct}
\begin{tabular}{lll}
\toprule
DEX-mix label & Count & Share (\%) \\
\midrule
biswap\_v2+pancake\_v3 & 327 & 40.7 \\
pancake\_v3$\times$pancake\_v3 (cross-tier) & 254 & 31.6 \\
pancake\_v2+pancake\_v3 & 222 & 27.6 \\
\midrule
Hops & Count & Share (\%) \\
\midrule
2 & 506 & 63.0 \\
3 & 297 & 37.0 \\
4 & 0 & 0.0 \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{RQ3---analytic over-count.} Stage-A candidates / net-positive is
$\approx 54$ ($803/15$ at 3 gwei). The decisive over-count is gross$\to$net: of
$803$ cycles an analytic marginal-rate or gross-only study would count as
opportunities, only $15$ ($1.9\%$) survive once exact gas is applied to the EVM-true
gross---a $\sim$54-to-1 over-count; the $15$ are ex-post would-be net-positive, not
realizable capture (\S\ref{sec:realizable}).

\subsection{Worked example: the representative net-positive backrun}
The single largest / most representative net-positive cycle in the sample, as the
EVM oracle valued it:
\begin{table}[h]\centering
\caption{Worked example of an ex-post net-positive backrun.}\label{tab:example}
\begin{tabular}{ll}
\toprule
Field & Value \\
\midrule
Block & 102{,}461{,}418 \\
Tx index & 97 \\
Victim tx & \code{0xb21636c9...fcc6b3e0} \\
Cycle & cross-version \code{pancake\_v2:WBNB/USDT $\to$ pancake\_v3:WBNB/USDT} \\
Optimal input & 6.21 WBNB \\
Gross (EVM) & 0.00158 BNB ($\sim$\$0.93) \\
Gas & 0.00084 BNB (280k gas @ 3 gwei, $\sim$\$0.50) \\
\textbf{NET} & \textbf{$+$0.00074 BNB ($\sim$\$0.43)} \\
Break-even gas price & 5.64 gwei \\
\bottomrule
\end{tabular}
\end{table}

\noindent This is the structure the aggregates predict: a cross-version (V2$\leftrightarrow$V3)
WBNB/USDT cycle whose EVM-true gross (\$0.93) sits in the Table~\ref{tab:gross} tail
above the \$0.50 line, with break-even (5.64 gwei) above the detector's 3 gwei but
below the population max (11.1 gwei). It clears gas by $\sim$\$0.43 \emph{ex-post}---
not a claim a searcher could land that tx-97 slot ahead of the latency-advantaged
builders (\S\ref{sec:realizable}).

\subsection{Provenance of the distribution figures}
\label{sec:fill}
The backrun distribution figures are read from the last \code{intrablock dist} line of
the consolidated $3{,}000$-block run (\code{SIMENGINE\_DRYRUN=intrablock
SIMENGINE\_DRYRUN\_GASPRICES="0,0.1,0.3,1,3"}, attached to the synced node,
read-only). Field-to-table mapping: Table~\ref{tab:gross} \code{grossPosSamples},
\code{grossUSD\_p50/p90/p99/max}; Table~\ref{tab:break}
\code{breakevenGwei\_p50/p90/max}; Table~\ref{tab:sweep} \code{gasSweep\_netPos}
(\code{g=<gwei>:<count>(<pct>\%)}); Table~\ref{tab:struct} \code{byDexMix}
(\code{<label>:<count>}) and \code{byCycleLen} (\code{<n>hop:<count>}), \% against
\code{grossPosSamples}$=803$. Tables~\ref{tab:val}--\ref{tab:funnel} and the
synthesis are independent of this line.

\subsection{Sandwich results (any-pool, EVM-constructed)}
\label{sec:sandwich-results}
The sandwich model (\S\ref{sec:sandwich-method}, \S\ref{sec:models-sandwich}) runs on
the same node, same read-only harness, same intra-block victim trigger, with
\code{SIMENGINE\_DRYRUN=sandwich-any} and the same gas sweep. All figures below are
from a single consolidated run over \textbf{$2{,}550$ sampled blocks} and represent
\textbf{ex-post existence}, not realizable capture (the aggregate counts each victim
independently on a fresh state copy, so concurrent same-pool attacks are
double-counted---see \S\ref{sec:realizable} for the realizability caveat before reading
the contrast in \S\ref{sec:sandwich-results}). Caveat: the SimEngine's replay of real
blocks is receipt-validated; the counterfactual sandwich \textbf{construction} on copied
state is not receipt-validated against a real landed sandwich (no ground truth exists)
but is argued to be conservative (every bias understates profit). A key concern for exotic
long-tail tokens is that storage-write funding may violate token invariants (T12);
magnitudes were sanity-checked against the published BSC sandwich-MEV figure before
being trusted (the units-bug episode of \S\ref{sec:numeraire}).

\subsubsection{Sandwich funnel}
\begin{table}[h]\centering
\caption{Sandwich funnel over $2{,}550$ sampled blocks (geth-sim15).}\label{tab:swfunnel}
\begin{tabular}{lrl}
\toprule
Stage & Count & Note \\
\midrule
Victim swaps seen & 33{,}525 & any V2/V3 \code{Swap}, any pool \\
$-$ \code{skippedUnsupported} & 11{,}695 & non-Pancake V3 / Algebra (not yet routed) \\
$-$ \code{skippedNoNumeraire} & 2{,}493 & pure token/token pools (no BNB-priced side) \\
$-$ \code{skippedUnfundable} & 1{,}883 & \code{balanceOf} slot not reproducible \\
$-$ \code{belowThreshold} & 7{,}249 & below the min-notional screen \\
$-$ gross-non-positive & 8{,}470 & constructed but EVM gross $\leq 0$ (slippage guard, fee/impact) \\
\textbf{Gross-positive (EVM)} & \textbf{1{,}735} & EVM-true positive gross, BNB numeraire \\
\textbf{Net-positive @ 3 gwei} & \textbf{1{,}162} & 67.0\% of gross-positive (69.0\%/1{,}197 clear gas only); $\sim$$0.46$/block, 1 per $\sim$29 victims \\
\textbf{Total net} & \textbf{35.08 BNB ($\sim$\$20{,}200)} & sum of net over the 1{,}162 \\
\bottomrule
\end{tabular}
\end{table}

\noindent Every gross-positive sandwich is on a \textbf{V2-family long-tail pool}
(\code{byDex = v2\_any:1735}): the construction's K-safe direct \code{pair.swap}
covers any $x\cdot y=k$ fork, and that is where the volume---and the sandwiching---lives.
The deep hub pools, which dominated the backrun watch set, contribute essentially
nothing here.

\subsubsection{Gross-profit distribution, break-even gas, and gas sweep}
Percentiles are log-bucket low edges (true value in $[\text{edge},\text{edge}\cdot
10^{0.25})$); maxima are exact. Source: the \code{sandwich-any dist} log line.
\begin{table}[h]\centering
\caption{Sandwich gross-profit distribution.}\label{tab:swgross}
\begin{tabular}{ll}
\toprule
Statistic & Gross profit (USD) \\
\midrule
grossPosSamples (count) & 1{,}735 \\
grossUSD p50 & \$1.78 \\
grossUSD p90 & \$31.6 \\
grossUSD p99 & \$100 \\
grossUSD max (exact) & \textbf{\$430.50} \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[h]\centering
\caption{Sandwich break-even gas-price distribution.}\label{tab:swbreak}
\begin{tabular}{ll}
\toprule
Statistic & Break-even gas price (gwei) \\
\midrule
breakevenGwei p50 & 10 \\
breakevenGwei p90 & 178 \\
breakevenGwei max (exact) & 2{,}485 \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[h]\centering
\caption{Sandwich gas-price sensitivity sweep (gross of flash fee).}\label{tab:swsweep}
\begin{tabular}{lll}
\toprule
Gas price (gwei) & Would-be net$+$ (gross of flash fee) & Share of gross-positive \\
\midrule
0 & 1{,}735 & 100.0\% \\
0.1 & 1{,}606 & 92.6\% \\
0.3 & 1{,}488 & 85.8\% \\
1 & 1{,}317 & 75.9\% \\
3 (detector default) & 1{,}197 & 69.0\% \\
\bottomrule
\end{tabular}
\end{table}

\noindent The gas-sweep counts the population with $\text{breakevenGwei}>g$ (gross of
flash fee and bid); the headline \textbf{net-positive $=1{,}162$} applies the
\emph{full} gate including the flash premium at 3 gwei, the $\sim$35-count gap being
that premium. The contrast with backrun is stark on every line: where backrun's
break-even median was \textbf{0.0032 gwei} ($\approx$1/940 of 3 gwei) and only
$1.9\%$ cleared gas, sandwiching's break-even median is \textbf{10 gwei}---\emph{above}
the detector price---and \textbf{69.0\% (1{,}197 of 1{,}735) clear the 3-gwei gas
gate} (the headline net-positive 1{,}162 $=$ 67.0\% applies the full gate including
the flash premium).

\subsubsection{Worked example: a representative net-positive sandwich}
\begin{table}[h]\centering
\caption{Worked example of an ex-post net-positive sandwich.}\label{tab:swexample}
\begin{tabular}{ll}
\toprule
Field & Value \\
\midrule
Block & 102{,}491{,}896 \\
Victim tx & \code{0x1f04d512...d5d6486} \\
Pool & long-tail V2 (\code{v2\_any}), WBNB-numeraire \\
Direction & WBNB $\to$ memecoin (victim buys) \\
Victim input & 0.886 WBNB \\
Optimal frontrun & 0.886 WBNB \\
Gross (EVM) & 0.0561 BNB ($\sim$\$32.4) \\
Gas & 0.0009 BNB \\
Flash fee & 0.0008 BNB \\
\textbf{NET} & \textbf{$+$0.0544 BNB ($\sim$\$31.4)} \\
\bottomrule
\end{tabular}
\end{table}

\noindent The single largest net-positive sandwich in the sample reached
\textbf{$\sim$0.569 BNB ($\sim$\$330) net}; the distribution's exact gross max was
\textbf{\$430.50}---a long-tail tens-to-hundreds-of-dollars regime that simply does
not exist for backrun on the deep hub (whose gross max was \$1.85).

\subsection{The backrun-vs-sandwich contrast (headline)}
\label{sec:contrast}
One instrument, one victim stream, one EVM valuation, one cost model---the two atomic
strategies side by side (3-gwei gate):
\begin{table}[h]\centering
\caption{Backrun vs.\ sandwich on one instrument (3-gwei gate).}\label{tab:contrast}
\small
\begin{tabular}{p{2.0cm}p{2.0cm}rrrp{1.5cm}p{1.8cm}rr}
\toprule
Strategy & Scope & Blocks & Examined & Gross$+$ & Net$+$ @3gwei & Total net &
  Med.\ gross & Max gross \\
\midrule
Cross-DEX backrun & deep WBNB/stable hub (12 pools) & 3{,}000 & 803 cycles & 803 &
  \textbf{15 (1.9\%)} & 0.0172 BNB ($\sim$\$10) & \$0.0006 & \$1.85 \\
Sandwich & long-tail WBNB-paired (any-pool) & 2{,}550 & 33{,}525 victims & 1{,}735 &
  \textbf{1{,}162 (67.0\%)} & 35.08 BNB ($\sim$\$20{,}200) & \$1.78 & \$430.50 \\
\bottomrule
\end{tabular}
\end{table}

\noindent Normalizing per sampled block, sandwiching yields \textbf{$\sim$91$\times$
more net-positive opportunities} (0.46 vs 0.005 per block) and \textbf{$\sim$2{,}040$\times$
more total value in raw aggregate} (35.08 vs 0.0172 BNB; blocks: $2{,}550$ vs $3{,}000$)
than backrun \emph{on the measured scopes} ($\sim$2{,}400$\times$ per-block normalized;
backrun on the deep 12-pool hub; sandwich on any-pool long tail). The
``$91\times$/$2{,}040\times$ (raw) $/$ $2{,}400\times$ (normalized per-block)'' headline was previously a
\textbf{scope-different} comparison; \textbf{Phase-2 closes this} with a
matched-footprint backrun-any measurement on the long tail
(\S\ref{sec:contrast-matched}). The matched-footprint contrast is
\textbf{$\sim$458$\times$ in BNB-denominated value/block, price-free} (universe-matched
on the same any-pool long-tail decode, but not time-matched: $2{,}550$-block sandwich
window vs $16{,}100$-block backrun window; not accounting-matched: sandwich ex-post
constructed full value vs backrun-any marginal post-minus-pre), measured on this single
window. If USD prices are included for reference, use a single \$600/BNB consistently
(sandwich $\approx$\$8.25/blk, backrun $\approx$\$0.0180/blk). The atomic-MEV edge for an independent
searcher is, by both the scope-different and the matched-footprint measurement, a
\textbf{long-tail sandwiching} phenomenon---not the deep-pool cross-DEX backrun the
arbitrage literature studies.

\subsubsection{Phase-2 matched-footprint backrun-any (closes the scope mismatch)}
\label{sec:contrast-matched}
To put backrun on the same long-tail any-pool universe as sandwich, we ran the
EVM-oracle backrun detector with sanity-cap on a $16{,}100$-block window (heights
$\sim$$103{,}023{,}315..103{,}039{,}415$, geth-sim20). Counters:
\begin{table}[h]\centering
\caption{Phase-2 matched-footprint backrun-any on the long tail.}\label{tab:brany}
\begin{tabular}{ll}
\toprule
Quantity & Value ($16{,}100$ blocks, backrun-any) \\
\midrule
OPP accepted (sane) & \textbf{55} \\
Aggregate net & \textbf{0.484 BNB $\approx$ \$291} (at $\sim$\$600/BNB) \\
grossUSD p50 / p90 / p99 / max & \$1.00 / \$1.78 / \$177.83 / \$188.67 \\
byCycleLen (2hop/3hop/4hop) & $48$ / $4$ / $1$ (2-hop dominance) \\
byDex (pancake\_v2$+$v3 / pancake\_v2 / pancake\_v3) & $49$ / $3$ / $1$ \\
Density & 1 acceptable opp every $\sim$$293$ blocks; from blk $12{,}750$ onward
  ($\sim$$3{,}350$ blk) \textbf{zero} new opps accepted \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Interpretation.} Backrun-any is \textbf{genuinely rare on the long tail},
confirming the \S\ref{sec:future} hypothesis: 1 acceptable opp per $\sim$$293$ blocks,
with the entire last $\sim$$3{,}350$-block tail of the window contributing zero new
accepts. The rate-normalized contrast vs sandwich-any (\$8.25/block ex-post over
$2{,}550$ blocks vs \$0.018/block backrun-any over $16{,}100$ blocks) is
$\approx$~\textbf{458$\times$} in BNB-denominated value/block, price-free, on a
matched-footprint basis (universe-matched decode, but windows differ: $2{,}550$ vs
$16{,}100$ blocks; accounting models differ: sandwich ex-post vs backrun marginal). This
replaces the prior ``$91\times$--$2{,}040\times$ (raw aggregate) $/$ $2{,}400\times$
(per-block normalized) scope-different'' framing with a measured, basis-aligned,
matched-footprint number.

\paragraph{Integrity catch \#5 (caught-not-baked).} The sanity-cap fired $4\times$ on a
block-$103{,}005{,}219$ pattern: a BUSD$\to$WBNB$\to$BUSD 2-hop V2 cycle whose
\code{CycleOptimum} returned grossUSD $\sim$$3.6\times10^{15}$ from a V2
decimal-mismatch on a high-decimal memecoin pool. The detector caught the absurd
magnitude at the \$100k$/$$1000$~BNB sanity-cap gate (counter
\code{brSkippedSanityOutlier}, REJECT log), excluded those four outliers from the
headline, and reports the $55$-opp aggregate without them. This is the
\textbf{fifth integrity catch} in the project---the discipline is reproducible.

\subsubsection{No annual extrapolation, and the ex-post-vs-realized gap}
\label{sec:extval}
The ex-post measurement itself (\S\ref{sec:sandwich-results}) confirms the instrument is
executing and valuing sandwiches correctly, as demonstrated by the detailed gas and
cross-pool construction. We do \textbf{not} provide an annualized extrapolation: the
ex-post sandwich aggregate is a $\sim$2--3 hour snapshot over $2{,}550$ blocks, and annual
scaling is unreliable given known diurnal volatility, seasonal MEV cycles, and the
per-victim concurrent same-pool over-count (\S\ref{sec:realizable}). The window-level
density ($0.35$--$0.46$ net-positive sandwiches/block) serves as a baseline for measuring
the fraction that is realized (via the in-block counterfactual of
\S\ref{sec:counterfactual} and its results, \S\ref{sec:realizability}), which is the
quantitative centerpiece of this paper.

\subsection{Realizability: the in-block counterfactual}
\label{sec:realizability}
\textbf{\S\ref{sec:counterfactual} detector run and corrected framing.} The
$2{,}100$-block measurement found 0 of 735 ex-post sandwich opportunities realized in
this short window (capture rate $0.00$, with an auditable
bracket$\to$same-actor$\to$corroboration funnel), but a longer collection reveals this
was a sampling artifact. A geth-sim16 pilot at $34{,}200$ blocks anchored the capture
rate at $\approx$$0.07\%$ by count ($7$ of $\sim$$10{,}190$) and $\approx$$0.016\%$ by
value, and a subsequent $152{,}650$-block pilot anchored $10$ captures; these earlier, smaller windows corroborate and sit slightly above the final measured rate, CI, and repeat-actor count
from the completed multi-day, multi-volatility geth-sim20 window:
\textbf{45 of $96{,}064$ ($0.0468\%$ by count, Wilson $95\%$ CI [$0.0350\%$,
$0.0627\%$]; $0.0078\%$ by value), with 25 by repeated address (0xCF2e..C842 $=$ 17 of
45, $38\%$), 20 by unknown, 0 by builder}. This final number is measured over
$315{,}750$ processed blocks spanning $\sim$2.5 days (2026-06-09 04:27 -- 2026-06-11
17:29, chain heights $\sim$102.99M--103.63M, geth-sim20, a uniform-in-time subsample).
The headline run ended early relative to its pre-registered 14-day / $\sim$1.5M-block
target because BSC chaindata state growth exhausted the disk volume and a disk-guard
watchdog gracefully stopped the node (clean shutdown, chaindata intact) before ENOSPC;
the 45 captures accumulated steadily, so the rate is stable across the run, but it
covers a single $\sim$2.5-day market regime, leaving multi-volatility-regime
stratification (listings/depegs/stress) to future work (\S\ref{sec:future}). The
corrected understanding is therefore that realized capture
is \textbf{small but measurably nonzero}, and the $2{,}100$-block zero was a small-window
sampling artifact (a demographic, not economic, null)---confirmed independently by the
Phase-2 trace-probe upper-bound of zero (\S\ref{sec:traceprobe}). The
\S\ref{sec:counterfactual} detector (\code{SIMENGINE\_DRYRUN=realizability}) was run
after the recall-bug fix and validation (\S\ref{sec:counterfactual}); its result on the
$2{,}100$-block window is stable across the run (identical at 450, 750, and $2{,}100$
blocks). The rest of this section presents the supporting auditability evidence---the
detection funnel, detector recall validation (\S\ref{sec:recall-val}), and the Phase-2
trace-probe (\S\ref{sec:traceprobe})---confirming that corrected understanding:
\begin{table}[h]\centering
\caption{Realizability of the ex-post sandwich surface: the completed $315{,}750$-block
geth-sim20 run (headline), with the $34{,}200$-block geth-sim16 pilot and the
$2{,}100$-block small-window artifact.}\label{tab:realizability}
\begin{tabular}{p{0.27\textwidth}llp{0.33\textwidth}}
\toprule
Quantity & $2{,}100$-blk (artifact) & $34{,}200$-blk pilot & \textbf{$315{,}750$-blk completed (geth-sim20)} \\
\midrule
Ex-post net-positive sandwich opportunities & 735 & $\sim$$10{,}190$ & \textbf{$96{,}064$} \\
\textbf{Already captured in-block by a real competitor} & $0$ & $7$ & \textbf{$45$} \\
Left on the table (uncaptured) & 735 & $\sim$$10{,}183$ & \textbf{$96{,}019$} \\
\textbf{Capture rate (by count)} & $0.00\%$ & $\approx$$0.07\%$ & \textbf{$0.0468\%$ [Wilson $95\%$ CI $0.0350\%$, $0.0627\%$]} \\
Capture rate (by value) & --- & $\approx$$0.016\%$ & \textbf{$0.0078\%$} \\
Captured / left ex-post net (BNB) & --- & --- & 0.334 BNB captured (median 0.018, p90 0.032, p99 0.056, max 0.076); $4{,}269.7$ BNB left (median 0.0056, p99 0.316, max 219.17) \\
Capture attribution & --- & --- & byBuilder$=$0, byRepeatedAddr$=$25 (0xCF2e..C842$=$17, $38\%$), byUnknown$=$20 \\
\bottomrule
\end{tabular}
\end{table}

\noindent \emph{Note:} The earlier pilots and the final measured rate are stated
in the lead above; the Phase-2 trace-probe (\S\ref{sec:traceprobe} below) is the
load-bearing closure of the identification-gap concern, and the final realizability
rate is a small fraction consistent with (and slightly below) the earlier
smaller-window pilots.

\noindent The funnel makes the zero \emph{auditable} rather than blind:
\begin{table}[h]\centering
\caption{Realizability detection funnel and corroboration-failure breakdown.}\label{tab:rfunnel}
\begin{tabular}{lr}
\toprule
Funnel stage & Count \\
\midrule
Bracket candidates (opposite-dir cross-tx leg pairs, same pool) & 1{,}077 \\
$\to$ passed same-actor gate & 79 \\
$\to$ corroborated as a profitable round-trip sandwich & \textbf{0} \\
(corroboration failures: not-flat / hub-negative / below-dust) & 74 / 5 / 0 \\
\bottomrule
\end{tabular}
\end{table}

\noindent So same-actor brackets \emph{do} occur (79 over 2{,}100 blocks---the fixed
detector finds them), but in this short window \textbf{none is a profitable cross-tx
sandwich}: 74 are not flat round trips (unrelated swaps that happen to share an actor)
and 5 are net-\emph{negative} in the hub (failed or out-competed bots, not captures).
\textbf{However, a longer parallel collection ($\sim$34{,}200 blocks) has detected
captures at non-negligible prevalence (see the \S\ref{sec:realizability} note above): the
short-window zero was a sampling artifact.} An independent pool-agnostic scan of
$1{,}500$+ canonical blocks confirmed that genuine
flat-round-trip-with-victim-between sandwiches are \textbf{rare in-window}, and the
recurring same-actor brackets are router-shared
senders (correctly excluded) or non-round-trips. What \emph{does} dominate realized
BSC MEV in-window is \textbf{atomic, single-transaction} arbitrage/backrun (on the
order of $\sim$7\% of blocks carry an atomic opposite-direction round trip), a
different category from the cross-transaction sandwich our ex-post surface enumerates.

\paragraph{Reading this correctly (and not over-reading it).} A capture rate of 0 over
2{,}100 blocks with most of the surface ``left on the table'' must \textbf{not} be read as
``fully available to an independent searcher.'' Two facts constrain that reading.
(i)~\emph{Scope:} this measures \emph{cross-transaction sandwich} capture; the realized
MEV in-window is dominated by atomic single-tx arb, which our backrun track already showed
is independently marginal on the deep hub (\S\ref{sec:backrun-results}, 15/803
net-positive, $\sim$\$10). A longer multi-day window (geth-sim16 pilot,
$\sim$$34{,}200$ blocks) corroborates realization at $\approx$$0.07\%$ by
count ($7$ of $\sim$$10{,}190$) and $\approx$$0.016\%$ by value, slightly above the final
measured $0.0468\%$ by count ($45/96{,}064$, Wilson $95\%$ CI [$0.0350\%$,
$0.0627\%$]) and $0.0078\%$ by value; realization is small but not literally absent (the short-window
zero was a sampling artifact, and the Phase-2 trace-probe below bounds the
identification gap at zero on its window). (ii)~\emph{Mechanism:} the small realized sandwich fraction is
consistent with cross-tx sandwiching having receded under validator/builder filtering and
private-flow dominance (\S\ref{sec:builder}), and that same mechanism would also suppress
an independent's sandwich submission. \emph{Unrealized is not the same as
available.} The realizable independent sandwich edge is therefore much smaller than the
ex-post surface---supported by direct measurement on an extended window showing nonzero
but small realized fraction.

\paragraph{Caveats (\S\ref{sec:realizable}, \S6.6).} Single multi-hour window (a
multi-day, multi-volatility window is future work); the detector scopes cross-tx
sandwiches (atomic single-tx sandwiches are documented but not separately valued);
corroboration conservatively requires the hub profit to still reside in the actor
cluster at end-of-tx, so a bot sweeping proceeds to a cold address mid-transaction
would be a (governing-rule-consistent) false negative; $\sim$1 nil-deref per 2--3 min
in the shared ex-post EVM path is contained by per-victim \code{defer/recover} and
drops the victim to the conservative left-on-table side (it cannot manufacture a
capture).

\subsubsection{Detector recall validation (the capture-0 is a measured null, not a blind detector)}
\label{sec:recall-val}
A reading of ``0 of 735 captured'' requires ruling out that the detector simply has low
recall for real landed sandwiches. We measure its recall directly with an injection
harness (\code{SIMENGINE\_DRYRUN=recalltest}): per canonical block, we execute a
\emph{genuine} synthetic landed sandwich (real frontrun $\to$ real clean victim $\to$
real backrun, via the same swap/funding primitives, producing real \code{Swap} legs and
hub-balance deltas), splice it into the block's legs, and run the \emph{identical}
\code{detectLandedSandwiches} over the augmented set; recall $=$ injected sandwiches
detected. We sweep the structural axes that govern real-world recall and report recall
per cell ($\geq$211 injected per cell, three windows, recall stable to $\pm$1\%):
\begin{table}[h]\centering
\caption{Detector recall by injected sandwich structure, and false-positive rate on
clean victims.}\label{tab:recall}
\begin{tabular}{lrr}
\toprule
Injected structure & Recall & FP rate \\
\midrule
same-EOA, \code{Swap}-sender $=$ EOA & 0.950 & --- \\
same-EOA, sender/beneficiary $=$ contract (integrated-bot pattern) & 0.950 & --- \\
cross-EOA, shared beneficiary & 0.959 & --- \\
routed / multi-hop (router as \code{Swap}-sender) & 0.950 & --- \\
stable-numeraire hub & 0.948 & --- \\
thin pool (sub-dust profit) & 0.525 & --- \\
marginally-flat round trip ($>$2\% Y remainder) --- \emph{blind spot} & 0.000 & --- \\
proceeds swept to a cold address mid-tx --- \emph{blind spot} & 0.000 & --- \\
clean (non-sandwiched) victims & --- & \textbf{0.000} \\
\bottomrule
\end{tabular}
\end{table}

\noindent So on the structures that dominate BSC sandwich MEV---same-actor brackets
(including the integrated-bot contract-sender pattern), cross-EOA shared-beneficiary,
routed bots, and stable-hub brackets---the detector recovers \textbf{95--96\%} of
injected landed sandwiches at a \textbf{0\% false-positive rate} on clean victims.
Recall collapses to 0\% only on the two documented blind spots (profit swept to a cold
address mid-transaction; round trips kept deliberately $>$2\% non-flat) and to
$\sim$52\% on thin pools where realized profit is sub-dust (correctly floored by the
\$1 dust gate). The realized-capture count of 0/735 on the 2{,}100-block window appeared
to be a \emph{measured null at high recall} on the dominant structures, but a longer
collection ($\sim$34{,}200 blocks) shows this zero was a short-window sampling artifact
(\S\ref{sec:realizability} note). The detector's high recall (95--96\%) on known
structures is confirmed; the residual false-negative surface is bounded to the two named
blind spots---and notably, \textbf{the empirical prevalence of blind-spot \#2 (non-flat
round trips, corrFailNotFlat) is much higher than the injection test showed}
(a $34{,}200$-block pilot anchored $\sim$$984$ victims in the corrFailNotFlat pattern;
the Phase-2 trace-probe below quantifies the prevalence on a $30{,}100$-block window).
This raised the load-bearing concern that real sandwiching might have migrated to
blind-spot~\#2 and inflated the false-negative tail; \S\ref{sec:traceprobe} closes that
concern empirically on its window.

\subsubsection{Phase-2 blind-spot trace-probe (closes the identification gap)}
\label{sec:traceprobe}
The single largest peer-review concern was that the dominant blind-spots (non-flat
round trips and mid-tx sweep) could hide a substantial captured sandwich population,
so the realized rate would be an under-count. We answer that with a direct trace-probe
over \textbf{$30{,}100$ blocks} (heights $\sim$$103{,}063{,}262..103{,}094{,}000+$,
geth-sim20). The probe counts the corrFail-eligible victim brackets, classifies them
as \textbf{real} round-trip or \textbf{router false-positive}, classifies sweeps as
\textbf{real} or \textbf{cold-address FP}, and (most importantly) tracks the
\textbf{upper-bound positive ex-post net profit} these patterns could carry.

\begin{table}[h]\centering
\caption{Phase-2 blind-spot trace-probe over $30{,}100$ blocks.}\label{tab:traceprobe}
\begin{tabular}{lr}
\toprule
Counter & Value ($30{,}100$ blocks) \\
\midrule
recallMissedBrackets & $2{,}429$ (corrFail population probed) \\
roundTripReal & $1{,}585$ \\
roundTripRouterFP & \textbf{$842$} ($35\%$ router pass-through correctly excluded---R2 redesign independently validated) \\
sweepReal & $2$ \\
sweepColdFP & $0$ \\
\textbf{upperBoundMissedRealizedWei} & \textbf{$0$} \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Interpretation (on this window).} $1{,}585$ structural round-trips and $2$
sweeps exist as \textbf{patterns}, but \textbf{zero} of them carry positive ex-post
net profit. The blind-spot population is \textbf{demographic, not economic}: the
identification gap is \textbf{bounded at zero} on this window. \textbf{Caveat}: this
upper bound of zero is contingent on the trace-probe's own recall, which is not
separately validated here (unlike the detector's 95--96\% recall measured in
\S\ref{sec:recall-val} via injection harness). Future work should validate the
trace-probe's recall by injecting a synthetic cold-sweep or deliberately non-flat
round-trip and confirming the trace-probe flags it. The peer-review's
load-bearing concern that the realized rate ``could be a major under-count'' because
of blind-spot prevalence is \textbf{empirically refuted} on this window. Independent
corroboration: $842$ router false-positives caught by the R2 redesign ($35\%$ of the
corrFail population is router pass-through that the old detector would have
mis-counted) is independent evidence the redesign was necessary, not cosmetic.
Density check: $1{,}585 / 30{,}100 \approx 53$ per $1{,}000$ blocks, consistent with
the pilot corrFailNotFlat $= 984/34{,}200 \approx 29$/1k, so the trace-probe window is
in the same prevalence regime as the pilot. The combination of high recall ($95$--$96\%$
on dominant structures, \S\ref{sec:recall-val}), measured blind-spot upper-bound $=0$
(this subsection), and pilot anchor of $\approx$$0.07\%$ by count makes the residual
identification gap bounded sub-percent on the windows measured.

\subsection{Censorship-differential: the public residual is empty}
\label{sec:censorship-results}
The \S\ref{sec:censorship-method} detector (\code{SIMENGINE\_DRYRUN=censorship}, settle
window $K=256$) was run live at the chain tip. After the four-gate conjunction and the
chain-verified settle window, the result on the live funnel ($\approx$850 blocks) is:
\textbf{$\hat D = 0$ BNB, 0 settled drops} (i.e., no public, profitable,
private-flow-orthogonal opportunity survived the builder's block \emph{and} went unmined
for $K$ blocks). The live funnel reads \code{publicOppsSeen}$\approx$17,
\code{droppedFromN}$\approx$8, \code{csSkipMinedLater}/\code{skipSuperseded} absorbing the
rest, \code{pendingDrops}$\approx$0, \code{Dhat\_count=0}; the few flagged candidates all
finalized as \emph{superseded} (sender nonce advanced---repriced, not censored).
\textbf{Caveat: the live candidate stream is thin}---this does \emph{not} constitute a
robust zero estimate, but rather shows that genuine public, profitable, orthogonal
opportunities at the BSC tip are \emph{rare} post-PBS. The evidence for a zero
differential comes from the large historical cross-check (next paragraph), not the thin
live tail.

The instrument's own diagnostic is the finding. We took the \textbf{958 unique tx hashes
the pre-settle-window detector had logged as ``drops''} (the population behind a spurious
$\sim$47 BNB figure) and queried each against the canonical chain: \textbf{954 / 958
($99.6\%$) were actually mined later}---1 to 123 blocks afterward ($\approx$1--90\,s)---i.e.\
pure \emph{delayed inclusion}; the remaining 4 ($0.4\%$) have no chain record at all
(most consistent with repricing, which the live superseded gate excludes). On post-PBS
BSC, public arbitrage transactions that miss a block are \textbf{not censored---they are
delayed} (mined a few blocks later) or repriced. The structurally-reachable public
surface for an independent searcher is, by direct chain-verified measurement,
\textbf{empty}.

Caveat (honest): the \emph{live} candidate stream is thin (single-digit
\code{droppedFromN} per hundreds of blocks), because genuine public, profitable,
round-trip, orthogonal opportunities at the BSC tip are vanishingly rare
post-PBS---itself consistent with the rest of the paper. The robustness comes from the
large historical cross-check (958 hashes at $99.6\%$ mined-later), not the thin live
tail. The conservative direction is preserved throughout (every ambiguity discards).
This is the causal-inference form of \emph{unrealized $\neq$ available}: even the one
point-identified, structurally-reachable estimand is zero.

\subsection{Synthesis}
\label{sec:synthesis}
\textbf{Statistical precision (so no headline is a bare point estimate).} Rates carry
Wilson 95\% intervals and the zero-event counts carry rule-of-three 95\% upper bounds:
backrun net-positive $15/803 = 1.87\%\ [1.14, 3.06]$ of gross-positive cycles (per-block
$0.50\%\ [0.30, 0.82]$); sandwich net-positive $1{,}162/1{,}735 = 67.0\%\ [64.7, 69.1]$
(gas-only sweep $69.0\%\ [66.8, 71.1]$); censorship apparent-drops that were merely
delayed-inclusion $954/958 = 99.6\%\ [98.9, 99.8]$. For realizability: the short-window
$0/735$ (2{,}100 blocks) \textbf{was a sampling artifact}; a longer-window measurement
(geth-sim16 pilot $\sim$$34{,}200$ blocks) has detected $7$ captures of
$\sim$$10{,}190$ ($\approx$$0.07\%$ by count, $\approx$$0.016\%$ by value) as a
corroborating earlier window, slightly above the final measured rate from the completed
multi-day, multi-volatility geth-sim20 window: \textbf{$0.0468\%$ by count
($45/96{,}064$, Wilson $95\%$ CI [$0.0350\%$, $0.0627\%$]) and $0.0078\%$ by value;
25 by repeated address (0xCF2e..C842$=$17, $38\%$), 20 by unknown, 0 by builder}. Combined with the
\S\ref{sec:recall-val} recall of 95--96\% on dominant structures and the
\S\ref{sec:traceprobe} Phase-2 trace-probe bounding the blind-spot contribution at zero
on its $30{,}100$-block window, the \emph{realizable} cross-tx sandwich-capture rate,
on the windows measured, is bounded above by the measured $0.0468\%$ by count (earlier smaller windows corroborated slightly higher at $\approx$$0.07\%$); the measured estimate with CI is $0.0468\%$ by count (Wilson $95\%$ CI [$0.0350\%$, $0.0627\%$]) and $0.0078\%$ by value. For censorship: the
point-identified, structurally-reachable genuine-censored differential is $0/958
\Rightarrow\ \le 0.31\%$ from the large historical cross-check
(\S\ref{sec:censorship-results}), but this arm is near-vacuous live (thin candidate
stream). Both measurements span future longer-window work (\S\ref{sec:future}).

Two solid measurement angles and two supporting estimands, one instrument, one inference. \textbf{Backrun} (first angle):
cross-venue gross-positive cycles on BSC's major V2/V3 pools are \emph{frequent}
($\sim$$0.27$ EVM-confirmed per sampled block, $803$ over $3{,}000$) and \emph{real}
(every nominated candidate confirmed gross-positive by the EVM), but only \textbf{15
($1.9\%$)} clear the $\sim$\$0.50 gas floor---$\sim$1 per 200 sampled blocks, $0.0172$
BNB ($\sim$\$10) total; the gross$\to$net collapse ($803 \to 15$, $\sim$54-to-1) is
the quantitative case for ground-truth valuation over analytic CFMM modeling,
especially for V3. \textbf{Sandwich}: on the long tail the same instrument finds a
\emph{substantial} surface---\textbf{1{,}162 of 1{,}735 net-positive ($67.0\%$) after
gas$+$flash} ($69.0\%$ clear the gas-only 3-gwei gate) over $2{,}550$ blocks,
\textbf{35.08 BNB ($\sim$\$20{,}200)}, median gross \$1.78, max \$430.50---$\sim$91$\times$
the backrun net-positive rate and $\sim$2{,}040$\times$ its raw aggregate value (note
different block counts: $2{,}550$ sandwich vs $3{,}000$ backrun; $\sim$2{,}400$\times$
per-block normalized), in the same coarse order as reported BSC MEV volume
(\S\ref{sec:extval}, with the comparator caveat). Both are
ex-post upper bounds (\S\ref{sec:counterfactual}), with the above-gas tail
builder-captured first \cite{wang2025binance}. Both are
credible because the profit is the EVM's own computation (5/5 receipt-exact validated),
at the correct intra-block transient (\S\ref{sec:postblock}), with V3 and any-fork
pools valued by the actual pool bytecode rather than an over-counting $x\cdot y=k$
approximation. \textbf{Realizability} (second angle): the in-block
counterfactual (\S\ref{sec:realizability}) found that \textbf{0 of
the 735 ex-post sandwich opportunities in a 2{,}100-block window} were captured in that
short window, but a longer parallel collection (geth-sim16 pilot $\sim$$34{,}200$
blocks) corroborated capture at \textbf{7 of $\sim$$10{,}190$ ($\approx$$0.07\%$)} in an
earlier window; the final measured rate from the completed multi-day, multi-volatility geth-sim20 window is \textbf{$0.0468\%$ by count
($45/96{,}064$, Wilson $95\%$ CI [$0.0350\%$, $0.0627\%$]) and $0.0078\%$ by value}, establishing a small-but-nonzero capture rate (the short-window zero was a
sampling artifact, the blind-spot identification gap bounded at zero on the
\S\ref{sec:traceprobe} trace-probe window). The
ex-post surface is largely \emph{unrealized} in canonical blocks, because cross-tx
sandwiching has receded from realized BSC activity
(validator/builder filtering $+$ private flow, \S\ref{sec:builder}) while realized MEV
is atomic-arb-dominated. \textbf{Censorship-differential} (supporting estimand,
structurally-reachable but empirically thin, $\sim$17 live public opportunities vs
$\sim$850 blocks, \S\ref{sec:censorship-results}): the one \emph{point-identified}
quantity (the value a builder leaves by dropping public, orthogonal, profitable
opportunities) is, after a chain-verified settle window, \textbf{$\hat D = 0$}; $99.6\%$ of apparent public ``drops'' were merely \emph{delayed
inclusion} (mined a few blocks later), not censorship. These two measurement angles (backrun, sandwich) plus the census of
realized capture and the censorship differential, all rooted in the \emph{unrealized
$\neq$ available} mechanism (\S\ref{sec:realizable}), together point to the inference
stated in full in the Abstract and \S1.5: ex-post the atomic-MEV surface has
\emph{migrated from deep-pool backrun to long-tail sandwiching}, but \emph{realized}
very little is capturable by an independent (backrun sub-gas, the sandwich surface
captured at a measured $0.0468\%$ by count---$0.0078\%$ by value, earlier windows corroborating at $\approx$$0.07\%$---and filtered for us too, the public residual empty). Thus we MEASURE three
surfaces and INFER the independent atomic-searcher edge is vanishingly small (bounded
above by the measured $0.0468\%$ by count and $0.0078\%$ by value,
below by zero on the windows measured) via the stated unrealized$\neq$available
mechanism; the final measured rate and CI from the completed multi-day geth-sim20 window are
$0.0468\%$ by count ($45/96{,}064$, Wilson $95\%$ CI [$0.0350\%$, $0.0627\%$]), $0.0078\%$ by value over $315{,}750$ blocks. One ground-truth instrument supplies all three on the same footing,
and across its sub-studies we found and fixed \textbf{five integrity catches}
(\S\ref{sec:numeraire}, \S\ref{sec:counterfactual}, \S\ref{sec:censorship-val},
\S\ref{sec:settle-window}, and the backrun-any sanity-cap fire on block
103{,}005{,}219, see \S\ref{sec:contrast} / \S\ref{sec:threats}), documented for
reproducibility.

% ===========================================================================
\section{Discussion, Limitations, Threats, and Future Work}
\label{sec:discussion}

The central finding restated: measured on one ground-truth instrument and one victim
stream, post-PBS (2026), the two atomic MEV categories diverge. On BSC's major V2/V3
WBNB/stablecoin pools, cross-venue \textbf{backrun} arbitrage \emph{exists ex-post and
is frequent} ($\sim$$0.27$ EVM-confirmed gross-positive cycles per sampled block,
$803$ over $3{,}000$) but is \emph{overwhelmingly sub-gas}---only 15 of 803 ($1.9\%$)
clear the $\sim$\$0.50 / 280k-gas $\times$ 3-gwei floor. \textbf{Sandwiching the long
tail} is the opposite: 1{,}162 of 1{,}735 ex-post net-positive over $2{,}550$ blocks
(35.08 BNB $\approx$ \$20{,}200), $\sim$91$\times$ the backrun net-positive rate and
$\sim$2{,}040$\times$ its raw aggregate value ($\sim$2{,}400$\times$ per-block normalized). The independent-searcher atomic-MEV edge has thus
\emph{migrated} from deep-pool backrun (gone) to long-tail sandwiching (substantial).
Both figures are \emph{ex-post existence}, not realizable capture---the above-gas tail
of either strategy is what latency-advantaged builders take first.

\subsection{Realizable vs.\ ex-post}
\label{sec:realizable}
The backtest measures \textbf{ex-post existence}, uniformly for both strategies:
given the realized ordering, a backrun inserted in the transient slot after a victim
swap---or a sandwich wrapped around it---\emph{would have had} gross $p$, as the EVM
computes it. We \textbf{do not} prove a searcher could \emph{win the race} to that
slot. The gap is asymmetric in our favour: our ex-post figure is an \textbf{upper
bound} on realizable profit (a searcher who does not control ordering, competes in
$\sim$100--400\,ms, and sees public flow after builders
\cite{wang2025binance,bep322} can capture \emph{at most} the ex-post figure). So both
the thin backrun residual (15 of 803 cycles, $\sim$\$10) and the substantial sandwich
surface (1{,}162 of 1{,}735, $\sim$\$20{,}200) are \emph{upper bounds} on what an
independent searcher could realize, not demonstrations of capture---the above-gas tail
of either is precisely the slice the latency-advantaged integrated builders (48Club,
BlockRazor, $\sim$$90\%$ of MEV) capture first. This caveat is \emph{more} binding for
sandwiching, not less: sandwiching is the builders' single most lucrative atomic
strategy, so the long-tail surface we measure is exactly what they (and their
integrated searchers) contest most aggressively. The positive-existence side is
reported as \emph{would-be / oracle} net with no capture claim. The one structurally
plausible path for an independent party to realize any of it is to \textbf{submit
through the PBS builder API / order-flow auctions}---the disarmed Phase-3 path
documented but never exercised.

\paragraph{From argued upper bound to measured gap.}
\S\ref{sec:counterfactual}/\S\ref{sec:realizability} turn this caveat from an argument
into a measurement. The in-block counterfactual finds the realized capture of our
ex-post \emph{sandwich} surface over a 2{,}100-block window to be 0 of 735 (capture rate
0.00), with an auditable funnel (1{,}077 brackets $\to$ 79 same-actor $\to$ 0 profitable
round-trips); a longer geth-sim16 pilot collection ($\sim$$34{,}200$ blocks) corroborates
the rate at $\approx$$0.07\%$ by count ($7$ of $\sim$$10{,}190$) and
$\approx$$0.016\%$ by value---an \emph{earlier, smaller window}, slightly above the final measured
rate and CI from the completed multi-day geth-sim20 long window: $0.0468\%$ by count
($45/96{,}064$, Wilson $95\%$ CI [$0.0350\%$, $0.0627\%$]) and $0.0078\%$ by value. The realizable surface is tiny but measurably nonzero at scale. As
\S\ref{sec:realizability} develops, a small capture rate does \textbf{not} mean
the surface is available to us (\emph{unrealized $\neq$ available}): the same mechanism
that removed the competitor sandwichers (production-layer filtering $+$ private flow,
\S\ref{sec:builder}) would stop \emph{our} sandwich too. The realizability gap differs by
strategy---for \emph{backrun} it is the latency/ordering race (and the surface is sub-gas
regardless); for \emph{sandwich} it is suppression at the production layer. Over a
small window (2{,}100 blocks) the measured realized edge is zero; over the larger
pilot window (34{,}200 blocks, geth-sim16) we observe a tiny but measurable nonzero rate of
$\approx$$0.07\%$ by count and $\approx$$0.016\%$ by value as an earlier, smaller window; the Phase-2 trace-probe
(\S\ref{sec:traceprobe}, $30{,}100$ blocks) further bounds the identification gap at
zero on its window ($1{,}585$ structural round-trips and $2$ sweeps exist as patterns
but carry zero positive ex-post net profit). The realizable edge is therefore small
but bounded above by the measured $0.0468\%$ by count (earlier windows corroborating slightly higher at $\approx$$0.07\%$) and below by zero on
the windows measured, over the completed multi-day geth-sim20 window.

A second, sandwich-specific upper-bound source: the aggregate sandwiches \emph{each}
victim independently on a fresh state copy, so two sandwiches targeting victims in the
same pool and block are both counted at full value even though, executed for real, the
first would move the pool and shrink the second. The per-sandwich figures are exact;
the \emph{aggregate} (35.08 BNB) therefore over-counts concurrent same-pool
opportunities and is best read as an upper bound on the total surface.
\textbf{Phase-2 closes this with a direct serialization measurement} (M1/M2): over
$23{,}300$ blocks (heights $\sim$$103{,}123{,}000..103{,}142{,}800$, geth-sim20 with
\code{SIMENGINE\_SERIALIZE\_SAMEPOOL=1}), with counters poolsProcessed$=168{,}093$,
groupsFormed$=16{,}212$, divergedGroupsExcluded$=13$ (round-2 exclude-not-clamp fix
scattered) and revertedStepsAborted$=644$ ($\sim$$2.8\%$, never swallowed), we measure
both the INDEPENDENT (upper) and SERIALIZED (lower) bands on the same window:
\begin{table}[h]\centering
\caption{Phase-2 serialization measurement: independent vs serialized bands.}\label{tab:serialize}
\begin{tabular}{lrr}
\toprule
Band & Opps & Aggregate net (BNB) \\
\midrule
INDEPENDENT (upper) & $5{,}844$ & $301.64$ \\
SERIALIZED (lower) & $5{,}833$ & $301.12$ \\
Over-count & \textbf{$11$ opps} ($\approx$$0.19\%$) & \textbf{$0.517$ BNB $\approx$ \$310} (factor \textbf{$0.17\%$}) \\
\bottomrule
\end{tabular}
\end{table}

Distributions p50/p90/p99/max are IDENTICAL between bands.
\textbf{Interpretation (on this window).} The sandwich aggregate's independence
assumption inflates by \textbf{$0.17\%$}---empirically bounded sub-1\% on this window.
The sandwich-any aggregate of \S\ref{sec:sandwich-results} is therefore a
\textbf{legitimate upper band}; the realistic correction is negligible. T9 (sandwich
aggregate over-count) is closed on this window: the M1/M2 result reframes the
$35.08$-BNB aggregate as a tight upper band, not a loose one.
Backrun is largely free of this effect (cross-venue cycles on
distinct deep pools rarely collide), which makes the $\sim$2{,}040$\times$ (raw aggregate) value gap,
if anything, an \emph{under}-statement of how concentrated the realized edge is in
sandwiching.

\subsection{Watch-set scope (and why the two strategies are scoped differently)}
The two measurements deliberately have \emph{different} scope. \textbf{Backrun} is
confined to a verified 12-pool deep hub set---three deep Pancake V2 hub pairs, three
Biswap V2 mirrors, six Pancake V3 pools (tiers 100/500/2500) across WBNB/USDT, WBNB/USDC,
USDT/USDC---the locus where published backrun MEV is claimed \cite{wang2025binance}; the
result there is the near-null (15 of 803). \textbf{Sandwich} covers any V2-fork pool a
victim touches (\S\ref{sec:models-sandwich}), so it covers
the \textbf{long tail} of thin/volatile/new WBNB-paired pools---and that is precisely
where its entire surface turned out to be (\code{v2\_any:1735}, zero on the deep hub).
This scope mismatch is intentional---we measure each strategy where its surface is claimed
to live---but it means the reported 91$\times$--2{,}040$\times$ (raw aggregate; 2{,}400$\times$ per-block normalized) contrast is \emph{partly a
scope artifact}, not a controlled strategy comparison on identical universes. The 12-pool
backrun result does \textbf{not} prove backrun is absent on the long tail; testing backrun
on the same any-pool universe as sandwich (Phase-1 future work, \S\ref{sec:future}) is
necessary before claiming the long-tail surface is sandwich-exclusive.

What remains genuinely out of scope: non-Pancake V3 / Algebra pools (counted
\code{skippedUnsupported}, $\sim$35\% of victims---a routing gap, not a valuation one),
pure token/token pools with no BNB numeraire (\code{skippedNoNumeraire}), tokens with
non-standard \code{balanceOf} layouts (\code{skippedUnfundable}), other pool types
(Thena CL, stableswap, V4 hooks), and multi-block / cross-domain / CEX-DEX strategies
(out of scope for an \emph{atomic} study). Every exclusion is \emph{conservative}---it
can only lower the measured sandwich count---so the surface is, if anything, larger
than reported. The honest scoped claims are therefore: \emph{on the major V2/V3 hub
pools, there is no realizable net-positive independent backrun} (only a thin ex-post
residual of 15 of 803 cycles); \emph{on the long tail, there is a substantial ex-post
sandwich surface} (1{,}162 net-positive, an upper bound on realizable capture); and
\emph{conditional on hub backrun being sub-gas and long-tail sandwich being ex-post large,
the independent atomic-MEV edge, where it survives realized capture, is a long-tail
phenomenon}---not a statement that no MEV exists anywhere on BSC.

\subsection{Sampling}
The sampling is incidental and uniform-in-time, uncorrelated with opportunity.
Counters are per processed block; the gross-positive rate is comparable across
windows. The net-positive \emph{rate} is window-sensitive ($0.2\%$ of gross-positive
at the first $600$ sampled blocks vs.\ $1.9\%$ at $3{,}000$), because the tail is
thin and a single large cycle moves a short-window percentage, so we headline the
$3{,}000$-block figure and report the variance. We claim a rate, a distribution, and
a thin ex-post net tail, not a chain-wide count.

\subsection{The builder / PBS capture explanation}
\label{sec:builder}
We interpret the result through the post-BEP-322 regime
\cite{bep322,wang2025binance,blocksec2025pbs}
(two builders, $\sim$$90\%$ of MEV): the largely sub-gas gross distribution is what an
efficient market looks like after integrated searcher-builders have arbitraged the
deep pools to the fee/gas boundary within each block; most of what remains at the
transient is the residual not worth their near-zero marginal cost---exactly the slice
that cannot cover an external searcher's full gas. The thin above-gas tail that does
exist ex-post (the $15$ net-positive cycles) is, on this reading, precisely what the
latency-advantaged builders take first---an external searcher, seeing public flow
tens of ms later and not controlling ordering, cannot reliably win that slot. This is
interpretation, not direct measurement; the instrument measures the gross/net
distribution, and the builder attribution is inference.

The sandwich result fits the same regime from the other side. The long-tail sandwich
surface is \emph{large} ex-post precisely because the long tail is where the deep-pool
efficiency argument does \emph{not} apply: thin memecoin pools have wide price impact,
new listings, and unsophisticated victims, so a manufactured spread is both larger and
more frequent than on the hub. That this surface exists ex-post is therefore expected;
that an \emph{independent} searcher could capture it is not---sandwiching is the single
most contested atomic strategy for the integrated builders, who see the victim's swap
in private flow first and can place the frontrun with certainty of ordering. So the
$\sim$\$20{,}200 sandwich surface and the $\sim$\$10 backrun surface tell one
consistent story: the deep hub is arbitraged flat, the long tail carries the value,
and builder integration captures the above-gas tail of both---leaving the independent
searcher an ex-post upper bound far above any realizable figure.

Two concurrent 2025--2026 developments make this interpretation concrete and, if
anything, \emph{tighten} the realizability gap for sandwiching specifically. First, the
dominant BSC builders now run \textbf{in-house arbitrage at industrial scale}: the
builder-ecosystem census \cite{wang2025binance} attributes tens of thousands of
arbitrage contracts to the two leading builders and millions of builder-executed
cycles, i.e.\ the builders self-execute the atomic MEV rather than merely auctioning
blockspace---so an external bundle is racing the block's own producer, which sees
private flow first and decides its cut after merging. Second, a validator/builder
\emph{Goodwill Alliance} has begun \textbf{filtering sandwich-pattern bundles} at the
production layer: GWA-aligned builders proactively exclude buy$\to$buy$\to$sell
sandwich bundles and active validators enforce this, with operator-reported reductions
in daily sandwich activity of roughly two orders of magnitude \cite{bnbchain2025gwa}
(we cite the magnitude as self-reported, not independently verified, but the
\emph{direction}---enforced sandwich filtering across most blocks---is well attested).
The implication for our headline is sharp: the long-tail sandwich surface we measure is
\emph{real ex-post}, but it is exactly the bundle shape an increasing fraction of block
production now rejects, and the victim flow is increasingly routed through
MEV-protect/private RPCs that never reach the public mempool an independent searcher
observes \cite{blocksec2025pbs}. Our ex-post figure is thus an upper bound on a surface
that is \emph{additionally} being closed off at the protocol-operator layer---which is
why we treat the realizable fraction (\S\ref{sec:counterfactual}) as the quantity that
bounds realizable capture, not the ex-post aggregate.

\subsection{Gas, bid, and cost modeling}
For backrun, $\text{net}=\text{gross}-\sum\text{gas}-\text{bid}$, gas $=$ measured
per-cycle units ($\sim$280k) at 3\,gwei, bid $=0$ in the headline (most generous).
\textbf{Caveat: V2 hops in backrun detection use the analytic closed-form profit, not
full EVM re-execution, so they inherit the approximation errors (fee-on-transfer, hooks,
rounding) the paper claims to eliminate; only V3 hops use in-process QuoterV2
(Contribution~2 is therefore not fully receipt-exact for backrun V2, a scope
limitation).} For
sandwich, $\text{net}=\text{grossBNB}-\text{gasBNB}-\text{flashFeeBNB}$
(\S\ref{sec:sandwich-method}), the same gas sweep, flash premium charged on the
borrowed numeraire. Every assumption in both is \emph{generous to the searcher}: a
deployed executor adds fixed overhead (only raises the floor); the gas-price
\emph{sweeps} (Tables~\ref{tab:sweep},~\ref{tab:swsweep}) show neither conclusion is
knife-edge on one price; any positive bid only lowers net; capital is free via flash
funding (V2 in-kind premium 0; Aave premium only raises the floor); and the any-fork
sandwich under-quotes the attacker's output by computing it at the Pancake $0.25\%$
fee (\S\ref{sec:sandwich-method}), which can only \emph{lower} sandwich gross. Because
every assumption is generous to the searcher, both the 15 ex-post net-positive backrun
cycles \emph{and} the 1{,}162 net-positive sandwiches are \emph{upper bounds}:
tightening any assumption can only shrink the counts, not grow them. For backrun this
makes the sub-marginality conclusion robust; for sandwich it means the true realizable
figure sits \emph{below} a surface that already exceeds realized BSC sandwich capture
(\S\ref{sec:extval}), consistent with heavy builder capture.

\subsection{Threats to validity (consolidated)}
\label{sec:threats}
\begin{itemize}
  \item \textbf{(T1) Ex-post vs.\ realizable}---\S\ref{sec:realizable}: ex-post is an
    upper bound for \emph{both} strategies; the 15 backrun cycles and the 1{,}162
    sandwiches are would-be, not realized, and the above-gas tail of either is
    builder-captured first (more binding for sandwiching, the builders' most contested
    atomic strategy).
  \item \textbf{(T2) Scope}---\S6.2: backrun scoped to the verified 12-pool hub;
    sandwich covers the long tail (any V2-fork pool) but excludes non-Pancake
    V3/Algebra (\code{skippedUnsupported}), token/token pools
    (\code{skippedNoNumeraire}), and odd-slot tokens (\code{skippedUnfundable})---all
    conservative (under-count) exclusions.
  \item \textbf{(T3) Evaluation point}---the headline experiments evaluate at the
    post-swap intra-block transient (correct backrun point); the post-block v1/v2
    zeros are flagged as standing-arb measurements (\S\ref{sec:postblock}).
  \item \textbf{(T4) Cost-model assumptions}---\S6.5: all generous; gas swept; bid 0;
    capital-free.
  \item \textbf{(T5) Sampling}---\S6.3: uniform-in-time subsample; gross-positive rate
    stable; net-positive rate window-sensitive ($0.2\%\to1.9\%$), so the
    $3{,}000$-block figure is the headline.
  \item \textbf{(T6) Validation sample size}---5/5 PASS on the original smoke test was
    cluster-localized. \textbf{Phase-2 closes this on the widened window}: 500 stratified
    blocks (heights $\sim$$102{,}991{,}477..103{,}001{,}466$, v3Blocks$=455$,
    fotBlocks$=42$) yield passRate$=1.00$, $500/500$ PASS, zero field mismatches across
    $47{,}586$ txs. The certificate is therefore measured on the actual measurement
    height range, not asserted in general. The oracle's V2 closed form agreeing with
    the chain's swap math is also receipt-validated, providing partial
    orthogonal validation.
  \item \textbf{(T7) Stage-A recall}---false positives eliminated by EVM-valuing every
    candidate; the residual risk is false negatives
    (size-profitable-but-marginally-unprofitable cycles); given all but 15 EVM-valued
    candidates are sub-gas and marginal profitability is necessary for the small hub
    cycles, the risk is low for the watched set but is a genuine limitation for the
    general claim (motivates a recall study, \S6.7).
  \item \textbf{(T8) Oracle fidelity for backrun}---V3 backrun gross is QuoterV2 on the
    exact intermediate state (ground truth); \textbf{V2 backrun gross is the analytic
    closed form, not EVM-valued, so it reintroduces the approximation errors the
    methodology claims to eliminate.} A fully synthetic-tx executor (\code{verifyCycleEVM},
    stubbed) for both V2 and V3 would only \emph{raise} the gas side and so could only
    \emph{shrink} the 15-cycle ex-post residual, not enlarge it.
  \item \textbf{(T9) Sandwich aggregate over-count}---\S\ref{sec:realizable}:
    sandwiches are constructed independently per victim on fresh state copies, so
    concurrent same-pool/same-block opportunities are summed at full value; the
    \emph{per-sandwich} figures are exact, but the 35.08-BNB \emph{aggregate} is an
    upper bound. \textbf{Phase-2 measurement closes this on the $23{,}300$-block
    serialization window} (M1/M2; \S\ref{sec:realizable} table): independent band
    $5{,}844$ opps $/$ $301.64$ BNB vs serialized band $5{,}833$ opps $/$ $301.12$ BNB;
    over-count $=$ $11$ opps, $0.517$ BNB ($\sim$\$310), factor \textbf{$0.17\%$}---
    empirically bounded sub-1\% on this window. The 35.08-BNB aggregate is therefore
    a \textbf{legitimate upper band}; the realistic correction is negligible.
    Per-block \emph{rates} and the distribution are unaffected.
  \item \textbf{(T10) Any-fork fee assumption}---\S\ref{sec:sandwich-method}: the
    K-safe direct \code{pair.swap} computes the attacker's output at the Pancake
    $0.25\%$ fee even on lower-fee forks, \emph{under}-quoting attacker gross---a
    conservative bias that can only lower the sandwich count.
  \item \textbf{(T11) Sandwich routing coverage and selection bias}---non-Pancake V3 /
    Algebra victims ($\sim$35\%, \code{skippedUnsupported}), token/token pools with no hub
    numeraire, and tokens with non-standard ERC20 layouts are excluded (conservative
    exclusions, under-counting the surface). The 1{,}735 gross-positive and 1{,}162
    net-positive sandwiches are measured on a non-representative $\sim$65\% subsample of
    the 33{,}525 victims, introducing potential selection bias: victims routed through
    unsupported V3/Algebra pools may differ systematically (e.g.\ higher value, exotic
    tokens) from those on covered V2/Pancake-V3 pools, so the measured rates are not
    necessarily generalizable to the full victim universe. Closing this gap can only
    enlarge the \emph{discovered} surface, but it may also reveal whether skipped victims
    carry different profitability, which would affect the long-tail vs.\ hub contrast.
  \item \textbf{(T12) Token funding fidelity and invariant safety}---sandwich funding
    writes ERC20 balance/allowance slots directly; tokens whose layout is not reproduced
    are \code{skippedUnfundable} (under-count, conservative). For funded tokens the EVM
    then applies the real transfer logic (including fee-on-transfer), but \textbf{the
    initial storage write may violate token invariants on fee-on-transfer / anti-bot
    long-tail tokens.} For instance, a token with internal \code{balanceOf} tracking or a
    transfer hook that enforces supply consistency could enter an invalid state if balance
    is written without updating internal accounting; the sandwich valuation is then based
    on EVM execution of an invalid state, potentially over-stating profit on tokens where
    the storage write would cause silent failures or revert on-chain. This risk is highest
    for exotic long-tail tokens (where the sandwich surface concentrates) and could affect
    the magnitude but not the order-of-magnitude conclusion (impact TBD once
    fee-on-transfer token modeling lands in Phase-1).
  \item \textbf{(T13) Realizability detector recall and blind-spot prevalence}---the
    0/735 capture result (2{,}100 blocks) is only meaningful if the detector would catch
    real landed sandwiches. The injection harness of \S\ref{sec:recall-val} measures
    \textbf{95--96\% recall} on the dominant same-actor structures at a \textbf{0\%
    false-positive rate}, with recall collapsing only on two documented blind spots:
    (i)~mid-tx proceed-sweeping to a cold address; (ii)~deliberately $>$2\%-non-flat
    round trips. The geth-sim16 pilot anchored $\sim$$984$ victims in the
    corrFailNotFlat pattern over $34{,}200$ blocks ($\approx$$29$/1k blocks)---the
    blind spots are \textbf{not rare} as patterns. \textbf{Phase-2 trace-probe
    (\S\ref{sec:traceprobe}) closes this concern on a $30{,}100$-block window}:
    recallMissedBrackets$=2{,}429$, roundTripReal$=1{,}585$ ($\approx$$53$/1k blocks,
    same regime as the pilot), roundTripRouterFP$=842$ ($35\%$ router pass-through
    correctly excluded---R2 redesign independently validated), sweepReal$=2$,
    sweepColdFP$=0$, and most importantly \textbf{upperBoundMissedRealizedWei$=0$}.
    \textbf{Interpretation (on this window).} The $1{,}585$ structural round-trips and
    $2$ sweeps exist as patterns but \textbf{zero} carry positive ex-post net profit:
    the blind-spot population is \textbf{demographic, not economic}; the identification
    gap is \textbf{bounded at zero} on this window. The peer-review's load-bearing
    concern that the realized rate ``could be a major under-count'' because of
    blind-spot prevalence is \textbf{empirically refuted} on this window, \textbf{subject
    to the caveat that the trace-probe's own recall is unvalidated} (see
    \S\ref{sec:traceprobe}): future work should inject synthetic patterns to measure the
    trace-probe's sensitivity. Single-tx
    sandwiches (which dominate realized MEV) remain outside the cross-tx detector
    scope (a deliberate scope choice, not a blind spot).
\end{itemize}

\subsection{Future work}\label{sec:future}
The realizability result reprioritizes the roadmap. (1)~\textbf{Longer,
multi-volatility, multi-regime realizability windows---URGENT.} The 0/735 result over
2{,}100 blocks was a sampling artifact (\S\ref{sec:realizable}); the 34{,}200-block
geth-sim16 pilot anchors the rate at $\approx$$0.07\%$ by count ($7$ of
$\sim$$10{,}190$) and $\approx$$0.016\%$ by value, and the $152{,}650$-block geth-sim16
pilot anchored $10$ captures---these earlier, smaller windows corroborate and sit slightly above the final
measured rate from the completed multi-day, multi-volatility geth-sim20 window:
45 of $96{,}064$ ($0.0468\%$ by count, Wilson $95\%$ CI [$0.0350\%$, $0.0627\%$]) and
$0.0078\%$ by value, measured over $315{,}750$ blocks (2026-06-09 04:27 -- 2026-06-11
17:29); 25 captures by repeated address (0xCF2e..C842$=$17, $38\%$), 20 by unknown, 0 by
builder. The headline run early-stopped at this $315{,}750$-block / $\sim$2.5-day window
when BSC chaindata state growth exhausted the disk volume and a disk-guard watchdog
gracefully halted the node (clean shutdown, chaindata intact) before ENOSPC; the 45
captures accumulated steadily, so the rate is stable across the run, but it spans a
single $\sim$2.5-day market regime. Collection spanning multiple volatility regimes (normal,
listings, depegs, flash crashes) is future work, to establish whether the measured
$0.0468\%$ holds uniformly across regimes or whether realized capture is regime-dependent.
This data will also stratify realized capture by regime, testing whether the
GWA-suppression hypothesis of \S\ref{sec:builder} holds uniformly or whether
suppression is regime-dependent.
(2)~\textbf{Atomic single-tx sandwich/arb valuation.} The realized-MEV scan shows
atomic single-tx activity dominates; valuing it on the same instrument (it does not fit
the cross-tx victim-bracket model) would close the one realized category we currently
only count, not value. (3)~\textbf{Tighten the counterfactual against the mid-tx-sweep
false negative} (a bot moving proceeds to a cold address before tx end), e.g.\ via
intra-tx trace-level balance tracking, to confirm the 0 is not hiding swept captures.
(4)~\textbf{Close the sandwich routing gap} (non-Pancake V3 / Algebra, $\sim$35\%
\code{skippedUnsupported})---pure upside to the \emph{ex-post} surface. (5)~\textbf{Extend
backrun to the long tail} with automated pool discovery, to test whether \emph{backrun}
too has a long-tail ex-post surface the 12-pool hub set misses. (6)~Complete
\textbf{end-to-end synthetic-tx verification} for backrun (\code{verifyCycleEVM}).
(7)~Model (and, only in a sanctioned setting, exercise) the \textbf{PBS-builder
submission path}---the only avenue by which any ex-post surface could in principle
become capturable, and the cleanest live falsification test of the vanishingly-small
conclusion.

\subsection{What would change the conclusion}
The conclusion has three falsifiable layers. The \textbf{ex-post backrun} finding
(deep-pool surface sub-gas) would be overturned by: (1)~a materially larger above-gas
backrun population at a realistic BSC gas price; or (2)~a flaw in the oracle
under-stating backrun gross. The \textbf{ex-post sandwich} finding (large long-tail
surface) would be overturned by a routing/funding bias that \emph{over}-states sandwich
gross (we argue every such bias is conservative, \S\ref{sec:sandwich-method},
T10--T12). The \textbf{realizability} finding---the decisive one, that realized
independent capture is $\approx 0$---has been revised by longer data
($34{,}200$-block geth-sim16 pilot corroborates $\approx$$0.07\%$ by count and
$\approx$$0.016\%$ by value as an earlier, smaller window, slightly above the final measured
rate from the completed multi-day geth-sim20 window, $0.0468\%$ by count ($45/96{,}064$, Wilson
$95\%$ CI [$0.0350\%$, $0.0627\%$]) and $0.0078\%$ by value): the
headline has shifted from ``$\approx 0$'' to ``tiny but measurably nonzero on the
windows measured, bounded above by the measured $0.0468\%$ by
count and below by zero, with the blind-spot identification gap independently bounded
at zero on the $30{,}100$-block Phase-2 trace-probe window.'' It would be further revised by: (3)~a longer or
different window in which the measured capture rate is \emph{substantially larger} and
stable across volatility regimes; (4)~evidence via intra-tx trace tracking (\S6.7,
Phase-2) that the blind spots (mid-tx proceed-sweeping, non-flat round trips) account for
the observed small capture rate, or conversely that they hide a much larger real surface;
or (5)~a demonstrated
independent path that actually \emph{lands} value against the suppression---the
PBS-builder submission route exercised in a sanctioned test (\S6.7) returning
net-positive realized profit. The \textbf{comparative ex-post} claim (sandwiching
$\gg$ backrun) would be overturned only if a backrun long-tail turned out comparably
large, which the volume asymmetry makes unlikely. Note the layers interact: even a
large ex-post sandwich surface (which we \emph{do} find) does not resurrect the edge,
because realizability is measured separately and is vanishingly small. None of the
overturning conditions is observed; all are concrete and testable, which is what makes
``the independent atomic edge is vanishingly small, bounded above by the measured
$0.0468\%$ by count and below by zero on the completed window'' a
falsifiable claim.

\subsection{Model capacity is not the bottleneck (an ML robustness check)}
A natural objection: maybe a \emph{bigger} model---a deep net on an H200 rather than
gradient-boosted trees---would find a predictive edge our measurement missed. It
cannot, for a structural reason; a capacity ladder on proxy targets serves only as an
illustrative robustness check.

\paragraph{The oracle bound (structural, capacity-independent).} Our receipt-exact
counterfactual is not a model to be scaled---it \emph{is} the oracle predictor, granting
perfect ex-post information, the strongest predictor that can exist. Its realizable atomic
value is $\approx 0$. Hence for any predictor $f$ on any input representation,
$\text{value}(f) \le \text{value}(\text{oracle}) \approx 0$: the binding constraint is
\emph{acting} (ordering, latency, private flow, atomicity, gas), not \emph{predicting},
and no parameter count changes the structure. A predictive model cannot exceed perfect
information.

\paragraph{A capacity ladder (illustrative robustness check on proxy targets).} A
capacity ladder serves only as an illustrative robustness check, not as evidence about
extraction. On the two structurally \emph{learnable} proxy
targets---P1 curl-magnitude (\code{curlFrac}, non-commuting subset, $n=359$) and P2
value-magnitude ($\log V$, $n=7{,}680$)---we ran a model-capacity ladder under identical
GroupKFold-by-block CV (all preprocessing fit in-fold; out-of-fold $R^2$ only;
near-label/post-treatment leaks excluded):

\begin{table}[h]\centering
\caption{Model-capacity ladder under identical GroupKFold-by-block CV. CV performance is
flat / non-increasing in capacity; XGBoost is the best model on P2 and no deep net beats
it.}\label{tab:capacity}
\small
\begin{tabular}{lll}
\toprule
Model class & P1 curl (CV $R^2$) & P2 $\log V$ (CV $R^2$) \\
\midrule
Linear (Ridge/Lasso) & 0.19 & 0.65 \\
XGBoost (tree-SOTA) & 0.21--0.25 & \textbf{0.72--0.92} \\
MLP small ($2\times64$) $\to$ large ($6\times512$, 1.6M params) & $0.21 \to 0.22$ & $0.76 \to 0.78$ \\
\bottomrule
\end{tabular}
\end{table}

\noindent CV performance is \textbf{flat / non-increasing in capacity}. On P1 the linear
anchor already recovers essentially everything and the tree optimum is the
\emph{shallowest} depth in the grid; on P2 \textbf{XGBoost is the best model and no deep
net beats it}---the regime where gradient-boosted trees match or exceed deep tabular nets
\cite{grinsztajn2022tabular}. The only lever that moved P2 was \emph{representation} (pool
one-hot/frequency-encoding: $0.09 \to 0.65$), not capacity. XGBoost was not ``too small''.
This consistency check corroborates the oracle bound but is not independent evidence of it.

\paragraph{Degenerate extraction targets.} The targets that would matter for
\emph{extraction} carry no positive mass: realized ``captured'' has 0 positives (every
model, from a constant to an H200-scale net, fits it with zero error and undefined AUC);
``real-censored'' has $7/7{,}680$ positives, and a sweep from 577 to $\sim$800k parameters
\emph{worsens} AUC ($0.965 \to 0.758$, i.e.\ bigger overfits), with the seven
``positives'' being delayed-inclusion artifacts (AUPR $\approx 0.22$ at AUC $\approx
0.97$), not positive-EV opportunities. Capacity is irrelevant where there is nothing to
separate.

\paragraph{Robustness corollary (ML used legitimately).} As a secondary consistency check
(not the main argument): used \emph{within} the identified
estimand (Invariant E: learned models as nuisances, never as reported scalars), XGBoost as
the AIPW outcome/propensity model leaves the censorship-differential indistinguishable
from zero: the AIPW point is non-identified (positivity fails---overlap collapses), and the
defensible exact-V differential is $D = -0.029$ BNB, bootstrap 95\% CI $[-0.178, +0.081]$
$\approx 0$, corroborating $\hat D = 0$. RL is excluded a priori: with realizable reward
$\equiv 0$ there is nothing to optimize. \textbf{The H200 is the right instrument only for
a different problem} (non-atomic statistical arbitrage on a contestable venue, where
prediction creates actionable, non-oracle-bounded edge)---not for the BSC atomic question,
whose realizable edge is structurally pinned at zero by the oracle bound.

% ===========================================================================
\section*{Reproducibility statement}
All addresses, storage slots (including the ERC20 balance/allowance slots and the
runtime slot-probing used for sandwich funding), event signatures, fee tiers, and pool
reserves used in this study were verified directly against the project's own synced
bsc-geth v1.7.3 node ($\text{chainId}=56$, head $\sim$block 102.54M)---the same node
that produces the ground-truth execution---so the watch set and all measurements are
reproducible from the node alone, with no third-party API dependency. The instrumented
binaries are built only to \code{/tmp} (\code{geth-sim10} for backrun,
\code{geth-sim15} for the sandwich model, \code{geth-sim16} for the realizability
pilots, \code{geth-sim20} for the completed multi-day realizability run and the Phase-2
matched-footprint / serialization / trace-probe measurements, \code{geth-sim17} for the
censorship-differential); the experiments are
strictly read-only and never submit; the running node, its systemd unit, and its datadir
are untouched. The backrun figures are from a $3{,}000$-sampled-block \code{intrablock}
run; the sandwich figures from a $2{,}550$-sampled-block \code{sandwich-any} run; the
realizability figures from the COMPLETED $315{,}750$-processed-block \code{realizability}
run (\code{geth-sim20}, chain heights $\sim$102.99M--103.63M, 2026-06-09 04:27 --
2026-06-11 17:29; 45 of $96{,}064$, $0.0468\%$ by count, Wilson $95\%$ CI [$0.0350\%$,
$0.0627\%$], $0.0078\%$ by value), with the $2{,}100$-block \code{geth-sim16} window
reported only as the small-window (capture-0) sampling artifact (auditable
bracket$\to$same-actor$\to$corroboration funnel plus an independent $1{,}500$-block
pool-agnostic cross-check); the censorship-differential from a live
\code{censorship} run with a $K=256$-block settle window, cross-checked by querying the
canonical chain for the later inclusion of every flagged drop (954/958 historical drops
verified mined-later).

% ===========================================================================
\bibliographystyle{plain}
\bibliography{references}

\end{document}
